### 2022-01-19 paper2.Rmd
git init

---
title: "Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations "
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::pdf_document2: 
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra)

rain <- read_rds(here('data', 'RAiN_vacc_clean.rds')) %>% 
  mutate(across(where(is.logical), as.factor),
         date = lubridate::as_date(EndDate))

my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')

## Automatically use showtext to render text
font_add_google("Open Sans", "open_sans")
showtext_auto()

theme_diss <- function(base_size = 14) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      # Figure assembly
      plot.title = element_text(family="open_sans",
                                size = rel(1), 
                                face = "bold",
                                margin = margin(0,0,5,0), 
                                hjust = 0),
      plot.title.position = "plot",
      plot.subtitle = element_text(family="open_sans",
                                   size = rel(0.85)),
      plot.caption = element_text(family="open_sans",
                                  size = rel(0.70),
                                  hjust = 1),
      # Graphical Zones
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Axes
      axis.title = element_text(family="open_sans", 
                                size = rel(0.85),
                                face = "bold"),
      axis.text = element_text(family="open_sans", 
                               size = rel(0.70), 
                               face = "bold"),
      axis.line = element_line(color = "black", 
                               arrow = arrow(length = unit(0.3, "lines"), 
                                             type = "closed")),
      # Legend
      legend.title = element_text(family="open_sans",
                                  size = rel(0.85), 
                                  face = "bold"),
      legend.text = element_text(family="open_sans", 
                                 size = rel(0.70), 
                                 face = "bold"),
      legend.key = element_rect(fill = "transparent", 
                                colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", 
                                       colour = NA),
      # Facetting 
      strip.background = element_rect(fill = "#17252D",
                                      color = "#17252D"),
      strip.text = element_text(family="open_sans",
                                size = rel(0.85), 
                                face = "bold", 
                                color = "white", 
                                margin = margin(5,0,5,0))
    )
}

theme_set(theme_diss())

```

# Intro
It is unclear how individuals choose to search for information through the
multimedia environment of the 21st century. Much of the research conducted in
social networks and communication focus on senders, influencers, and persuasion
strategies (Merton 1968) rather than on “the receiver as an active information
seeker and processor. " (Johnson and Meischke 1993).

Core discussion networks are the default lens to investigate network resources
and social support in surveys. The underlying assumption is that individuals
reach out to a handful of strong ties when in need of support, which can be
elicited in surveys using name generators (Marsden 1987). This approach has
yielded important insights, but largely overlooks crucial processes of resource
activation (Hurlbert, Haines, and Beggs 2000; Perry and Pescosolido 2015; Smith
2005). Small (2017) shows that the core discussion network does not capture how
people activate social support in practice and indicates that people draw on
much broader social connections for support, also calling back to the weak ties
research by Granovetter (1973). There is ongoing research investigating how
weak-tie support holds for different support types based on the architecture put
forward by House, Umberson, and Landis (1988) of instrumental, emotional, and
informational support (Legewie and Gonzalez 2020). I follow the definition of
Cohen and Wills (1985) and define informational support as “help in defining,
understanding,  and coping with problematic events and include education,
advice, or referral to another source of  support” (Winemiller et al. 1993:640).

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
*f the most convenient vehicles for information search. While Small (2017)
focuses on how support can depend on a network tie simply "happened to be
there", online search is theoretically the most frictionless and costless mode
*f support. There are three computer-mediated vehicles I consider for this
analysis: search engines like Google, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
*r Twitter. The first two comprise what I call “online search”, while the third
is conceptually distinct and important to include in the survey; yet, it is a
hybrid of social network activation and online search.

As online search or interaction also allows increased anonymity, no or lowered
social cost, and the potential avoidance of embarrassment and other negative
social interactions, I theorize that a majority of people who searched for
information will have done so online.

For this paper, I will use the case of Covid-19 vaccinations to explore the
variation among information search vehicles. There are theoretical reasons why
individuals would choose to search for information among their network ties
instead of online search. For instance, Rains (2018) finds that patients tend to
search for technical information about an illness online but turn to their
social network for experiential information from others facing similar
circumstances in the case of cancer. Moreover, if an individual distrusts the
medical establishment, or popular media, they may be more likely to activate
informational support among their social network or turn to online groups that
validate their worldview (Bogers and Wernersen 2014).

This research project is important because the vehicles used to search by people
impacts the information they are exposed to. Given the large swaths of both
misinformation and disinformation regarding Covid-19 (Motta, Stecula, and
Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and
the measurable impacts this misinformation has had on pandemic-related health
behaviors, how we choose to search for information affects our own lives and the
lives of others. Moreover, individuals who do not utilize social networks for
information search may feel like they have no network support, leading to
feelings of network isolation with major implications for mental health (Thoits
2011).

## section B: Research Questions
* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
* What factors lead people to perform health information search online versus among social network ties? 
* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?

# Research Methodology
The data used for this research project are based on original survey data sampled between `r format( min(rain$date), '%B %d, %Y')`  through `r format(max(rain$date), '%B %d, %Y')`.
- grant sample
- MTurk
- Dates 
- Locations

## Descriptive Statistics

###  Dependent Variables 
search for info
int_sought_

search for info by type
int_sought_fr_pers  
int_sought_fr_dr    
int_sought_fr_onlgroup
int_sought_fr_onlnet
int_sought_fr_onlsearch

vaccination view
vacc_view_pos

### Independent Variables
 receive_i_fr_dr   
receive_i_fr_pers      
receive_i_fr_tv    
receive_i_fr_onlnet    
receive_i_fr_onlgroup

age 
gender 
race_white   
race_black    
race_nat      
race_asian 
hispanic
college

I received a $7,193 grant from the Summer Institute of Computational Social
Science to conduct research on network activation. Because I am co-PI on this
grant with my colleague Nicolas Legewie (University of Pennsylvania,
Humboldt-University of Berlin), I established permissions early-on in our
planning process to introduce and ‘own’ a few specific survey questions for
independent research on network versus non-network information activation.

The majority of this survey is a replication of the survey conducted in Mario
Small’s Book, Someone to Talk To (2017). We aim to expand on Small’s finding
that people draw on much broader sources than “important people” for support by
investigating how this theory of weak-tie support holds for different support
types (instrumental, emotional, and informational support; (see House et al.
1988)).

We aim to conduct surveys with 900 participants. The sample population for our
main survey are adult, non-institutionalized US residents. To adjust for the
non-representative sample provided by Amazon Mechanical Turk where we will host
the survey, we will use post-stratification weights based on the demographic
profile of each respondent (Wang et al. 2015).

```{r desc-table-1}
#| results = "asis"

desc_table <- rain %>% 
  select(receive_i_fr_dr,
  receive_i_fr_pers,
  receive_i_fr_tv,
  receive_i_fr_onlnet,
  receive_i_fr_onlgroup,
  int_sought,
  int_sought_fr_pers,
  int_sought_fr_dr,
  int_sought_fr_onlgroup,
  int_sought_fr_onlnet,
  int_sought_fr_onlsearch,
  int_sought_affect,
  vacc_status,
  vacc_view_pos,
  race_white,
  race_black,
  race_nat,
  race_asian, 
  hispanic,
  college,
  age, receive_i) %>% 
  as.data.frame()

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, Black` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Some College, or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")))
```

```{r desc-table-2}
#| results = "asis"

datasummary(formula = ((`Income` = income)+  
                         (`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful)) ~ N + Percent(), 
 data = rain,
   fmt = '%.2f',
  title = 'Descriptive Statistics for Categorical Variables',
 notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

# TODO reorder factors in categorical table

```

```{r clean_before_reg}
rain <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(1, 0))))

regression_labels = c(
  'receive_i_fr_dr0' = 'Received Info, Doctor',
  'receive_i_fr_pers0' = 'Received Info, Person',
  'receive_i_fr_tv0' = 'Received Info, News',
  'receive_i_fr_onlnet0' = 'Received Info, Social Networking Site',
  'receive_i_fr_onlgroup0' = 'Received Info, Online Forum',
  'int_sought0' = 'Sought Info',
  'int_sought_fr_dr0' = 'Sought Info, Doctor',
  'int_sought_fr_pers0' = 'Sought Info, Person',
  'int_sought_fr_onlnet0' = 'Sought Info, Social Networking Site',
  'int_sought_fr_onlgroup0' = 'Sought Info, Online Forum',
  'int_sought_fr_onlsearch0' = 'Sought Info, Online Search',
  'age' = 'Age',
  'gender=Male' = 'Gender, Male',
  'gender=Other' = 'Gender, Other',
  'college0' = 'Some College +',
  'race_white0' = 'White',
  'race_black0' = 'Black',
  'race_nat0' = 'Native American',
  'race_asian0' = 'Asian',
  'hispanic0' = 'Hispanic or Latino/x')
```

# What predicts someone intentionally searched for information

Q171 And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.

* Yes
* No

```{r model1-table}
#| results = "asis"

mod1 <- glm(formula = int_sought ~ 
              receive_i_fr_dr +   
              receive_i_fr_pers +   
              receive_i_fr_tv +   
              receive_i_fr_onlnet +   
              receive_i_fr_onlgroup +   
              age + 
              gender + 
              race_white +   
              race_black +    
              race_nat +      
              race_asian +  
              hispanic  + 
              college,
            data = rain, family = binomial)

# library(patchwork)
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_pers") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_tv") + 
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup")

modelsummary(mod1,
            gof_omit = 'AIC',
            # stars = TRUE,
            estimate = "{estimate}{stars}",
            title = 'What predicts someone intentionally searched for information',
            coef_map = regression_labels,
            notes = 'Exponentiated Coefficients',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

```

```{r model1-plot}
#| fig.cap='Plot of Coefficients, Model 1'

plot_summs(mod1, 
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             'Some College +' = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'What predicts someone intentionally searched for information', caption = 'Coefficients Scaled and robust') +
  theme_diss()
```
\newpage

# What is associated with using different kinds of search vehicles?

Q172 How did you look for information about the Covid-19 vaccine?

*	Asking a person like friend, neighbor, or family member that I know  
*	Asking my doctor or another health professional  
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  
*	Searched for my question using an online search engine such as Google or Bing   
*	Other ________________________________________________

```{r model2-table}
#| results = "asis"

part2_models <- list()

part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Online Forum']] <- glm(formula = int_sought_fr_onlgroup ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Social Networking\nSite']] <- glm(formula = int_sought_fr_onlnet ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Online Search']] <- glm(formula = int_sought_fr_onlsearch ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

modelsummary(part2_models,
             estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = 'Note: Exponentiated Coefficients',
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

# TODO ADD IN N To TABLE

```

\newpage

# Researching how you search for vaccination information affects vaccination status
```{r model3-table}
#| results = "asis"

mod3 <- glm(formula = vacc_view_pos ~ receive_i_fr_dr +   
           receive_i_fr_pers +      
           receive_i_fr_tv +    
           receive_i_fr_onlnet +    
           receive_i_fr_onlgroup + 
           int_sought_fr_pers +  
           int_sought_fr_dr +    
           int_sought_fr_onlgroup +
           int_sought_fr_onlnet +
           int_sought_fr_onlsearch +
           age + 
           gender + 
           race_white +   
           race_black +    
           race_nat +      
           race_asian + hispanic +     
           college,  
         data = rain, family = binomial)

modelsummary(mod3,
            gof_omit = 'AIC',
            estimate = "{estimate}{stars}",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = 'Note: Exponentiated Coefficients',
            coef_map = regression_labels,
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')
```

```{r model3-plot}
#| fig.cap='Plot of Coefficients, Model 3'

plot_summs(mod3,
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             'Some College +' = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'Does receiving or searching for information predict vaccination status?', 
       caption = 'Coefficients Scaled and robust') +
  theme_diss()

# library(patchwork)
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup") + 
# sjPlot::plot_model(m, type = "pred", terms = "int_sought_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "college") 
```

# Bibliography

# Appendix 1: Survey Questions

*Q181*: Now, we're going to transition a bit to ask you about the information you received during the Covid-19 pandemic.

*Q170*: In the past 12 months, without searching for it, did you receive information about the Covid-19 vaccine from … (check all sources you received information from)

*	your doctor or other health professional?   (1) 
*	a person like friend, neighbor, or family member that you know ?  (9) 
*	From television news channel or the newspaper?  (10) 
*	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
*	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
*	Other  (13) ________________________________________________

*Q171*: And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.

*	Yes  (4) 
*	No  (5)

*Q172*: How did you look for information about the Covid-19 vaccine?

*	Asking a person like friend, neighbor, or family member that I know  (1) 
*	Asking my doctor or another health professional  (4) 
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  (6) 
*	Searched for my question using an online search engine such as Google or Bing  (7) 
*	Other  (8) ________________________________________________

*Q173*: What sort of information did you search for? 
 Separate different topics with a comma or semi-colon. 
___________

*Q174*: How useful was the information you found?

*	Extremely useful  (22) 
*	Very useful  (23) 
*	Moderately useful  (24) 
*	Slightly useful  (25) 
*	Not at all useful  (26)

*Q175*: Did the information you learned affect your decision to get vaccinated against Covid-19?

*	Yes  (39) 
*	No  (40)

*Q179*: Did you receive a Covid-19 vaccine?

*	Yes  (9) 
*	No  (10) 
*	I'm unsure or would not like to respond  (11)

*Q180*: Do you plan to receive a vaccine for the prevention of the Covid-19 virus?

*	Definitely not  (9) 
*	Probably not  (10) 
*	Might or might not  (11) 
*	Probably yes  (12) 
*	Definitely yes  (13) 
*	I would not like to respond  (14)

*gender*: What is your gender?

*	Male  (1) 
*	Female  (2) 
*	Other  (3) ________________________________________________
*	Prefer not to say  (4)

*hispanic*: Are you Hispanic, Latino/a/x, or Latin American Origin?

*	Yes  (1) 
*	No  (2)

*race*: What is your race? If you are "mixed race", select all that apply.

*	White  (1) 
*	Black or African American  (2) 
*	American Indian or Alaskan Native  (3) 
*	Asian (please specify):  (4) ________________________________________________
*	Other (please specify):  (5) ________________________________________________
*	Prefer not to say  (6)

*educ*: What is the highest level of education that you have completed?

*	Less than high school  (1) 
*	High school graduate  (2) 
*	Some college  (3) 
*	Associate's or Technical degree  (4) 
*	Bachelor's degree  (5) 
*	Graduate or professional degree  (6)

*income*: We would be interested to know roughly what your total household income
before taxes is. We mean income from all sources, including welfare, stock
dividends, other household members' income, etc. In 2020, in which bracket did your total family income fall?

*	Under $1,000  (1) 
*	\$1,000 to \$9,999   (2) 
*	\$10,000 to \$19,999  (3) 
*	\$20,000 to \$29,999  (4) 
*	\$30,000 to \$39,999  (5) 
*	\$40,000 to \$49,999  (6) 
*	\$50,000 to \$59,999  (7) 
*	\$60,000 to \$74,999  (8) 
*	\$75,000 to \$89,999   (9) 
*	\$90,000 to \$109,999  (10) 
*	\$110,000 to \$129,999  (11) 
*	\$130,000 to \$149,999  (12) 
*	\$150,000 or over  (13) 
*	Don't know  (14)

*age*: What is your age? (in years)

________________________________________________________________

### 2022-01-19 data_cleaning.R

@@ -1,0 +1,155 @@
+pacman::p_load(tidyverse, here)
+
+#load Full Data
+clean_data <- read_rds(here('data', 'qualtrics_fullsurvey_clean_2021-12-11.rds')) %>% 
+  mutate(across(where(is.factor), as.character))
+
+
+### Load Batch rejection data ###
+mturk_batches <-
+  mutate(read_csv('data/Batch_1_results.csv', show_col_types = FALSE), batch = 1) %>% 
+  bind_rows(mutate(read_csv('data/Batch_2_results.csv', show_col_types = FALSE), batch = 2)) %>% 
+  bind_rows(mutate(read_csv('data/Batch_3_results.csv', show_col_types = FALSE), batch = 3)) %>% 
+  bind_rows(mutate(read_csv('data/Batch_4_results.csv', show_col_types = FALSE), batch = 4)) %>% 
+  bind_rows(mutate(read_csv('data/Batch_5_results.csv', show_col_types = FALSE), batch = 5)) %>% 
+  filter(AssignmentStatus == "Rejected")
+
+### Remove Rejected Data ###
+
+to_factor <- c('int_sought',
+               'int_sought_useful',
+               'int_sought_affect',
+               'vacc_status',
+               'vacc_status_future',
+               'gender', 
+               'race',
+               'educ',
+               'income',
+               'employment',
+               'hispanic')
+
+clean_data <- clean_data %>% 
+  anti_join(mturk_batches, by= c("MID" = "WorkerId")) %>% 
+  select(ResponseId, MID, EndDate,
+         receive_i_fr = Q170,             
+         receive_i_fr_oth = Q170_13_TEXT,
+         int_sought = Q171,
+         int_sought_fr = Q172,       
+         int_sought_fr_oth = Q172_8_TEXT,      
+         int_sought_what = Q173,        
+         int_sought_useful = Q174,        
+         int_sought_affect = Q175,            
+         vacc_status = Q179,             
+         vacc_status_future = Q180,
+         age, gender, race, race_5_TEXT, hispanic, educ, income, employment) %>% 
+  
+  # Clean up variable types 
+  mutate(across(to_factor, as_factor),
+         vacc_status = case_when(vacc_status == "Yes" ~ TRUE,
+                                 vacc_status == "No" ~ FALSE,
+                                 TRUE ~ NA)) %>%
+  
+  # race,  cleaning
+  mutate(race_white   = str_detect(race, 'White'),
+         race_black   = str_detect(race, 'Black'),
[…]

### 2022-01-21 paper2.Rmd
Data section done

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra)
+pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra, scales)
 
@@
 
+conf_int_prop <- function(var){
+  p <- mean(!!var, na.rm = T)
+  q <- 1 - p
+  n <- nrow(rain)
+  min <- p - 1.96*sqrt((p*q)/n)
+  max <- p + 1.96*sqrt((p*q)/n) 
+  paste0(round(min, 2), ", ", round(max, 2))
+}
+
+print_perc <- function(var){
+  label_percent()(mean(var, na.rm = T))
+}
+
+side_by_side <- function(models, ...) {
+    estimates <- c("Coef." = "{estimate}{stars}", 
+                       "Std.Error" = "({std.error})")
+    models <- rep(models, each = length(estimates))
+    estimates <- rep(estimates,
+                     times = length(models)/length(estimates))
+
+    alignment <- paste(rep('l', length(models) + 1), collapse = '')
+
+    names(models) <- names(estimates)
+
+    modelsummary(models = models, 
+                 estimate = estimates,
+                 statistic = NULL,
+                 align = alignment, ...)
+}
 ```
@@
 social networks and communication focus on senders, influencers, and persuasion
-strategies (Merton 1968) rather than on “the receiver as an active information
-seeker and processor. " (Johnson and Meischke 1993).
+strategies [@mertonManifestLatentFunctions1968] rather than on “the receiver as
+an active information seeker and processor."
+[@johnsonComprehensiveModelCancerRelated1993].
 
@@
 reach out to a handful of strong ties when in need of support, which can be
-elicited in surveys using name generators (Marsden 1987). This approach has
-yielded important insights, but largely overlooks crucial processes of resource
-activation (Hurlbert, Haines, and Beggs 2000; Perry and Pescosolido 2015; Smith
-2005). Small (2017) shows that the core discussion network does not capture how
-people activate social support in practice and indicates that people draw on
+elicited in surveys using name generators [@marsdenCoreDiscussionNetworks1987].
+This approach has yielded important insights, but largely overlooks crucial
+processes of resource activation [@hurlbertCoreNetworksTie2000;
+@perrySocialNetworkActivation2015; @smithDonPutMy2005]. Small
+[-@smallSomeoneTalk2017] shows that the core discussion network does not capture
+how people activate social support in practice and indicates that people draw on
 much broader social connections for support, also calling back to the weak ties
-research by Granovetter (1973). There is ongoing research investigating how
-weak-tie support holds for different support types based on the architecture put
-forward by House, Umberson, and Landis (1988) of instrumental, emotional, and
-informational support (Legewie and Gonzalez 2020). I follow the definition of
-Cohen and Wills (1985) and define informational support as “help in defining,
-understanding,  and coping with problematic events and include education,
-advice, or referral to another source of  support” (Winemiller et al. 1993:640).
+research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
+research investigating how weak-tie support holds for different support types
+based on the architecture put forward by House, Umberson, and Landis
+[-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
+informational support. I follow the definition of Cohen and Wills
+[-@cohenStressSocialSupport1985] and define informational support as “help in
+defining, understanding,  and coping with problematic events and include
+education, advice, or referral to another source of  support”
+[@winemillerMeasurementStrategiesSocial1993, p. 640].
 
@@
 modern human life, it makes sense that performing online search has become one
-*f the most convenient vehicles for information search. While Small (2017)
-focuses on how support can depend on a network tie simply "happened to be
-there", online search is theoretically the most frictionless and costless mode
-*f support. There are three computer-mediated vehicles I consider for this
-analysis: search engines like Google, posting questions on online forums like
-subreddits or Facebook groups, and posting a status update online via Facebook
-*r Twitter. The first two comprise what I call “online search”, while the third
-is conceptually distinct and important to include in the survey; yet, it is a
-hybrid of social network activation and online search.
+*f the most convenient vehicles for information search. While Small
+[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
+simply "happened to be there", online search is theoretically the most
+frictionless and costless mode of support. There are three computer-mediated
+vehicles I consider for this analysis: search engines like Google, posting
+questions on online forums like subreddits or Facebook groups, and posting a
+status update online via Facebook or Twitter. The first two comprise what I call
+“online search”, while the third is conceptually distinct and important to
+include in the survey; yet, it is a hybrid of social network activation and
+online search.
 
@@
 individuals would choose to search for information among their network ties
-instead of online search. For instance, Rains (2018) finds that patients tend to
-search for technical information about an illness online but turn to their
-social network for experiential information from others facing similar
-circumstances in the case of cancer. Moreover, if an individual distrusts the
-medical establishment, or popular media, they may be more likely to activate
-informational support among their social network or turn to online groups that
-validate their worldview (Bogers and Wernersen 2014).
+instead of online search. For instance, Rains
+[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
+technical information about an illness online but turn to their social network
+for experiential information from others facing similar circumstances in the
+case of cancer. Moreover, if an individual distrusts the medical establishment,
+or popular media, they may be more likely to activate informational support
+among their social network or turn to online groups that validate their
+worldview [@bogersHowSocialAre2014].
 
@@
 impacts the information they are exposed to. Given the large swaths of both
-misinformation and disinformation regarding Covid-19 (Motta, Stecula, and
-Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and
+misinformation and disinformation regarding Covid-19 [@mottaHowRightLeaningMedia2020; @pathakInfodemicsCOVID19Role2020; @shahsavariConspiracyTimeCorona2020] and
 the measurable impacts this misinformation has had on pandemic-related health
@@
 information search may feel like they have no network support, leading to
-feelings of network isolation with major implications for mental health (Thoits
-2011).
+feelings of network isolation with major implications for mental health 
+[@thoitsMechanismsLinkingSocial2011]
 
@@
 # Research Methodology
-The data used for this research project are based on original survey data sampled between `r format( min(rain$date), '%B %d, %Y')`  through `r format(max(rain$date), '%B %d, %Y')`.
-- grant sample
-- MTurk
-- Dates 
-- Locations
-
-## Descriptive Statistics
-
-###  Dependent Variables 
-search for info
-int_sought_
-
-search for info by type
-int_sought_fr_pers  
-int_sought_fr_dr    
-int_sought_fr_onlgroup
-int_sought_fr_onlnet
-int_sought_fr_onlsearch
-
-vaccination view
-vacc_view_pos
-
-### Independent Variables
- receive_i_fr_dr   
-receive_i_fr_pers      
-receive_i_fr_tv    
-receive_i_fr_onlnet    
-receive_i_fr_onlgroup
-
-age 
-gender 
-race_white   
-race_black    
-race_nat      
-race_asian 
-hispanic
-college
-
-I received a $7,193 grant from the Summer Institute of Computational Social
-Science to conduct research on network activation. Because I am co-PI on this
-grant with my colleague Nicolas Legewie (University of Pennsylvania,
-Humboldt-University of Berlin), I established permissions early-on in our
-planning process to introduce and ‘own’ a few specific survey questions for
-independent research on network versus non-network information activation.
-
-The majority of this survey is a replication of the survey conducted in Mario
-Small’s Book, Someone to Talk To (2017). We aim to expand on Small’s finding
-that people draw on much broader sources than “important people” for support by
-investigating how this theory of weak-tie support holds for different support
-types (instrumental, emotional, and informational support; (see House et al.
-1988)).
-
-We aim to conduct surveys with 900 participants. The sample population for our
-main survey are adult, non-institutionalized US residents. To adjust for the
-non-representative sample provided by Amazon Mechanical Turk where we will host
-the survey, we will use post-stratification weights based on the demographic
-profile of each respondent (Wang et al. 2015).
+The data used for this research project are based on original survey data
+sampled between `r format( min(rain$date), '%B %d, %Y')`  through 
+`r format(max(rain$date), '%B %d, %Y')`. This survey was hosted on Qualtrics and
+participants were paid and recruited using Amazon Turk (MTurk). The total valid
+survey responses (n = `r nrow(rain)`) were selected from a total of 1,066
+respondents; some responses were disqualified due to a few factors such as
+detected usage of a VPN, random answer clicking (determined by illogical
+responses), poor quality typed responses (e.g. social network alters
+consistently named random nouns), or taking the survey more than once. The same
+is slighted gender unbalanced, slightly skewing towards a male sample. For the
+respondents who provided their zipcode (p = 
+`r round(nrow(rain[!is.na(rain$region),]) / nrow(rain), 2)`), the 
+sample is quite balanced with a slight skew towards MTurkers in the South (p = 
+`r round(nrow(rain[rain$region == 'South',]) / nrow(rain), 2)`). 
+The survey took an average of `r round(mean(rain$duration), 2)` minutes with a 
+standard deviation of `r round(sd(rain$duration), 2)` minutes. The shortest 
+valid survey took `r round(min(rain$duration), 2)` minutes and the longest took 
+`r round(max(rain$duration), 2)` minutes. Participants were paid \$6.00 for their 
+time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
+Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
+Science and the Russell Sage Foundation. The main portion of this survey
+replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expandingon
+Small’s finding that people draw on much broader sources than “important people”
+for support by segregating weak-tie social support into instrumental, emotional,
+and informational support (see House et al. 1988)). The latter part of the
+survey focuses on resource activation for the specific case-study of information
+during the Covid-19 pandemic and is analyzed in this paper.
 
@@
   title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
-  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")))
+  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
+  output = "kableExtra") %>% 
+  kable_styling(latex_options = c("hold_position", "striped"))
+
 ```
+
+## Measures
+
+###  Sought Information
+There are multiple dependent variables of interest for this paper. The first
+variable is a dichotomous indicator of whether someone intentionally sought out
+information about Covid-19 vaccinations. The survey asked, "And how about you 
+yourself intentionally looking for information about a Covid-19 vaccine? Such 
+information can include things such as advice, clarification, facts, and
+experiences". About `r print_perc(rain$int_sought)` ($\widehat{p}$)
+of respondents had intentionally sought out information about Covid-19 
+vaccinations (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought)`\}).
+
+Further dependent variables segment the above question into multiple options;
+"How did you look for information about the Covid-19 vaccine?". Respondents were
+posed with 5 responses and 'other', of which they could select multiple. The
+largest proportion, `r print_perc(rain$int_sought_fr_dr)`, asked their 
+'doctor or another health professional' (95% Confidence Interval = 
+\{`r conf_int_prop(rain$int_sought_fr_dr)`\}).
+About `r print_perc(rain$int_sought_fr_pers)`  said they asked 'a person 
+like friend, neighbor, or family member that [they] know' (95% Confidence 
+Interval = \{`r conf_int_prop(rain$int_sought_fr_pers)`\}). An additional
+`r print_perc(rain$int_sought_fr_onlsearch)` searched 'for [their] question 
+using an online search engine such as Google or Bing' (95% Confidence Interval 
+= \{`r conf_int_prop(rain$int_sought_fr_onlsearch)`\}). About a quarter of the 
+sample, `r print_perc(rain$int_sought_fr_onlgroup)`, 'posted queries in an 
+online discussion group, listserve, or other online forum like a Facebook Group 
+or Subreddit' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlgroup)`\}).
+And finally, `r print_perc(rain$int_sought_fr_onlnet)` of the sample 'posted queries 
+on a social networking site such as Facebook timeline, Twitter status update, or 
+Linkedin' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
+Much of the question wording and the specific categories of search were inspired
+by ICPSR project 37220 [@scanlon19].
 
@@
 
-datasummary(formula = ((`Income` = income)+  
+datasummary(formula = (
+  # (`Income` = income)+  
                          (`Gender` = gender)+  
@@
                          (`Plan to be Vaccinated if not` = vacc_status_future)  +
-                         (`Found Info Sought Useful` = int_sought_useful)) ~ N + Percent(), 
+                         (`Found Info Sought Useful` = int_sought_useful) +
+                         (`Census Region` = region)) ~ N + Percent(), 
  data = rain,
@@
  output = "kableExtra") %>%
-  kable_styling(latex_options = 'HOLD_position')
+  kable_styling(latex_options = c("hold_position", "striped"))
 
@@
 ```
+
+### Vaccination Outlook
+
+```{r}
+vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
+  group_by(col = vacc_status_future) %>% 
+  summarise(n = n()) %>%
+  mutate(n = n / sum(n))
+```
+Another Dependent variable for this analysis is a dichotomous variable
+indicating whether the respondent has received a vaccination against Covid-19 or
+plans to. For this survey, the number of doses were unimportant and actually
+having already received the dose were irrelevant to the research question. This
+variable instead focuses on intent or opinion about the vaccine. About 
+`r print_perc(rain$vacc_view_pos)` have a positive view about the vaccine. This
+construct is made through the combination of  two survey items. The first item
+is actual vaccination status, obtained through the question 'Did you receive a
+Covid-19 vaccine?'. `r print_perc(rain$vacc_status)` of the sample said that
+they had indeed received a vaccination (95% Confidence Interval = \{
+`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
+closer to 55% (CITE), this indicates some bias in our sample that must be
+acknowledged: either MTurkers are more likely to be vaccinated that the normal
+population (sampling bias) or there is some conformity bias in the responses
+causing survey takers to provide false answers. The second survey item that
+contributes to 'Vaccination Outlook' was only given to those who had not
+responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
+plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
+who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
+`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
+said they were 'definitely yes' getting the vaccine; 
+`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
+said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
+`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
+said they 'Might or might not', 
+`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
+said 'Probably not', and finally
+`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
+said they would 'definitely not' receive the vaccine. The variable 'Vaccination
+Outlook' indicates their either the respondent received a Covid-19 vaccine or
+either probably or definitely will in the future.
+
+### Independent Variables
+The first independent variables used in this analysis are based on the question, 
+'In the past 12 months, without searching for it, did you receive information
+about the Covid-19 vaccine from … (check all sources you received information
+from)'. This differs from the 'How did you look for information' question above
+because it is based on passive reception of information. The largest proportion
+of respondents had received information from a person like friend, neighbor, or
+family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
+). Respondents also commonly received information from a television news channel
+or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
+`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
+their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
+received information from a social networking site such as Facebook timeline,
+Twitter status update, or linkedin. Finally, the lowest proportion of the sample
+had received information from an online discussion group, listserve, or other
+online forum like a Facebook group or subreddit 
+($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).
+
+We also asked various demographic questions to understand our sample. The 
+average age of our sample was `r round(mean(rain$age, na.rm = T), 2)`. 
+Our sample was `r label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
+female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
+male. The sample is diverse racially though some ethnic groups are under
+represented compared to national averages. Race was evaluated using the
+question, 'What is your race? If you are "mixed race", select all that apply.'
+Because of the multi-selection question, each variable is dichotomous and
+proportions are shown. `r print_perc(rain$race_white)` of the sample claimed
+they were 'White', `r print_perc(rain$race_black)` claimed to be 'Black or
+African American', `r print_perc(rain$race_nat)` chose 'American Indian or
+Alaskan Native', `r print_perc(rain$race_asian)` selected 'Asian', and finally 
+when asked ' Are you Hispanic, Latino/a/x, or Latin American Origin?', 
+`r print_perc(rain$hispanic)` selected 'Yes'. Respondents were also asked to 
+select the  highest level of education that you have completed. Based on the 
+breakdown between 'Less than high school', 'High school graduate', 'Some college',
+'Associate's or Technical degree', 'Bachelor's degree', and 'Graduate or 
+professional degree',  `r print_perc(rain$college)` of the sample were classified
+to have a College-level education (Associate's degree or above).
+
+My analytic strategy proceeds in four steps. In Tables X & Y, I present descriptive
+statistics for all study variables, including variable ranges, means, and standard
+deviations.
+
+In Table 3, I fit a model of state mobility scores using robust regression with the M estimator and iterated re-weighted least squares (IWLS) to downweight the influence of outliers (Jorgenson 2007; Venables and Ripley 2002).
+Model
+1 regresses state mobility scores on dummy variables for week. This model tests
+whether mobility scores vary across the 8-week study period. We use dummy variables for week to capture thresholds in the association between week and mobility.
+Model 2 adjusts for state religiosity, median age, percent black, the unemployment
+rate, population density, and the mobility lag. This model tests whether state religiosity is associated with state mobility scores net of state demographic characteristics
 
@@
                   race_asian, 
-                  college), ~ factor(.x, levels = c(1, 0))))
+                  college), ~ factor(.x, levels = c(0, 1))))
 
 regression_labels = c(
-  'receive_i_fr_dr0' = 'Received Info, Doctor',
-  'receive_i_fr_pers0' = 'Received Info, Person',
-  'receive_i_fr_tv0' = 'Received Info, News',
-  'receive_i_fr_onlnet0' = 'Received Info, Social Networking Site',
-  'receive_i_fr_onlgroup0' = 'Received Info, Online Forum',
-  'int_sought0' = 'Sought Info',
-  'int_sought_fr_dr0' = 'Sought Info, Doctor',
-  'int_sought_fr_pers0' = 'Sought Info, Person',
-  'int_sought_fr_onlnet0' = 'Sought Info, Social Networking Site',
-  'int_sought_fr_onlgroup0' = 'Sought Info, Online Forum',
-  'int_sought_fr_onlsearch0' = 'Sought Info, Online Search',
+  'receive_i_fr_dr1' = 'Received Info, Doctor',
+  'receive_i_fr_pers1' = 'Received Info, Person',
+  'receive_i_fr_tv1' = 'Received Info, News',
+  'receive_i_fr_onlnet1' = 'Received Info, Social Networking Site',
+  'receive_i_fr_onlgroup1' = 'Received Info, Online Forum',
+  'int_sought1' = 'Sought Info',
+  'int_sought_fr_dr1' = 'Sought Info, Doctor',
+  'int_sought_fr_pers1' = 'Sought Info, Person',
+  'int_sought_fr_onlnet1' = 'Sought Info, Social Networking Site',
+  'int_sought_fr_onlgroup1' = 'Sought Info, Online Forum',
+  'int_sought_fr_onlsearch1' = 'Sought Info, Online Search',
   'age' = 'Age',
@@
   'gender=Other' = 'Gender, Other',
-  'college0' = 'Some College +',
-  'race_white0' = 'White',
-  'race_black0' = 'Black',
-  'race_nat0' = 'Native American',
-  'race_asian0' = 'Asian',
-  'hispanic0' = 'Hispanic or Latino/x')
+  'college1' = 'Some College +',
+  'race_white1' = 'White',
+  'race_black1' = 'Black',
+  'race_nat1' = 'Native American',
+  'race_asian1' = 'Asian',
+  'hispanic1' = 'Hispanic or Latino/x')
 ```
@@
 
+# mod1 = list(mod1)
+
+# side_by_side(mod1, 
+#              gof_omit = 'AIC',
+#              title = 'What predicts someone intentionally searched for information',
+#             coef_map = regression_labels,
+#             notes = 'Exponentiated Coefficients',
+#             exponentiate = TRUE,
+#             output = "kableExtra") %>%
+#   kable_styling(latex_options = c("HOLD_position", "striped"))
+
 modelsummary(mod1,
-            gof_omit = 'AIC',
-            # stars = TRUE,
-            estimate = "{estimate}{stars}",
+            gof_omit = 'AIC', statistic = NULL,
+            estimate = "{estimate}{stars} ({std.error})",
             title = 'What predicts someone intentionally searched for information',
@@
  output = "kableExtra") %>%
-  kable_styling(latex_options = 'HOLD_position')
+  kable_styling(latex_options = c("HOLD_position", "striped"))
 
@@
 # What is associated with using different kinds of search vehicles?
-
-Q172 How did you look for information about the Covid-19 vaccine?
-
-*	Asking a person like friend, neighbor, or family member that I know  
-*	Asking my doctor or another health professional  
-*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  
-*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  
-*	Searched for my question using an online search engine such as Google or Bing   
-*	Other ________________________________________________
 
@@
 modelsummary(part2_models,
+             align="llllll",
+             statistic = NULL,
             estimate = "{estimate}{stars}",
@@
             output = "kableExtra") %>%
-  kable_styling(latex_options = 'HOLD_position')
+  kable_styling(latex_options = c("scale_down", "HOLD_position", "striped"))  %>%
+  add_header_above(c(" " = 1, "Dependent Variable" = 5))
 
-# TODO ADD IN N To TABLE
+# 
+# 
+# 
+# 
+# side_by_side(part2_models, 
+#              gof_omit = 'AIC',
+#             coef_map = regression_labels,
+#             notes = 'Note: Exponentiated Coefficients',
+#             title = 'What predicts someone intentionally searched for information, by vehicle of information search',
+#             exponentiate = TRUE,
+#             output = "kableExtra") %>%
+#   kable_styling(latex_options = c("HOLD_position", "striped")) %>% 
+#   add_header_above(c(" ", 
+#                      "Person" = 2,
+#                      "Doctor" = 2, 
+#                      "Online Forum" = 2,
+#                      "Social Networking\nSite" = 2,
+#                      "Online Search"  = 2)) %>%
+#   add_header_above(c(" " = 1, "Dependent Variable" = 10)) %>%
+#   kableExtra::landscape()
 
@@
 
+# 
+# mod3 = list(mod3)
+# 
+# 
+# side_by_side(mod3, 
+#              gof_omit = 'AIC',
+#             title = 'Does receiving or searching for information predict vaccination status?',
+#             notes = 'Note: Exponentiated Coefficients',
+#             coef_map = regression_labels,
+#             exponentiate = TRUE,
+#             output = "kableExtra") %>%
+#   kable_styling(latex_options = c("HOLD_position", "striped"))
+#
+
 modelsummary(mod3,
-            gof_omit = 'AIC',
-            estimate = "{estimate}{stars}",
+            gof_omit = 'AIC', statistic = NULL,
+            estimate = "{estimate}{stars} ({std.error})",
             title = 'Does receiving or searching for information predict vaccination status?',
@@
             output = "kableExtra") %>%
-  kable_styling(latex_options = 'HOLD_position')
+  kable_styling(latex_options = c("HOLD_position", "striped"))
 ```
@@
              'Gender, Other' = 'gender=Other',
-             'Some College +' = 'college',
+             "Associate's Deg or above" = 'college',
              'White' = 'race_white',
@@
            robust = TRUE) +
-  labs(title = 'Does receiving or searching for information predict vaccination status?', 
+  labs(title = 'Does receiving or searching for information predict vaccination sentiment?', 
        caption = 'Coefficients Scaled and robust') +
@@
 
-# Bibliography
+\newpage
+# References {-}
 
+<div id="refs"></div>
+
+\newpage
 # Appendix 1: Survey Questions
 
+-------------------------------------------------
+
 *Q181*: Now, we're going to transition a bit to ask you about the information you received during the Covid-19 pandemic.
+
+-------------------------------------------------
 
@@
 *	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
-*	Other  (13) ________________________________________________
+*	Other  (13) _______
+
+-------------------------------------------------
 
@@
 *	No  (5)
+
+-------------------------------------------------
 
@@
 *	Searched for my question using an online search engine such as Google or Bing  (7) 
-*	Other  (8) ________________________________________________
+*	Other  (8) ___________
+
+-------------------------------------------------
 
@@
  Separate different topics with a comma or semi-colon.
-___________
+
+-------------------------------------------------
 
@@
 
+-------------------------------------------------
+
 *Q175*: Did the information you learned affect your decision to get vaccinated against Covid-19?
@@
 *	No  (40)
+
+-------------------------------------------------
 
@@
 *	I'm unsure or would not like to respond  (11)
+
+-------------------------------------------------
 
@@
 
+-------------------------------------------------
+
 *gender*: What is your gender?
@@
 *	Female  (2) 
-*	Other  (3) ________________________________________________
+*	Other  (3) ________________
 *	Prefer not to say  (4)
+
+-------------------------------------------------
 
@@
 
+-------------------------------------------------
+
 *race*: What is your race? If you are "mixed race", select all that apply.
@@
 *	American Indian or Alaskan Native  (3) 
-*	Asian (please specify):  (4) ________________________________________________
-*	Other (please specify):  (5) ________________________________________________
+*	Asian (please specify):  (4) _______
+*	Other (please specify):  (5) _______
 *	Prefer not to say  (6)
+
+-------------------------------------------------
 
@@
 *	Graduate or professional degree  (6)
+
+-------------------------------------------------
 
@@
 
+-------------------------------------------------
+
 *age*: What is your age? (in years)
-
-________________________________________________________________

### 2022-01-21 data_cleaning.R

@@ -28,8 +28,13 @@ to_factor <- c('int_sought',
                'employment',
                'hispanic')
 
+zips <- vroom::vroom(here('data', 'all_us_zipcodes.csv')) %>% 
+  left_join(vroom::vroom(here('data', 'us census bureau regions and divisions.csv')), by = c('state' = 'State Code'))  %>% 
+  select(zipcode = code, state, region = Region, division = Division)
+
 clean_data <- clean_data %>% 
   anti_join(mturk_batches, by= c("MID" = "WorkerId")) %>% 
+  filter(ResponseId != 'R_3FXzD9yMC1LpHHd') %>% 
   select(ResponseId, MID, EndDate,
          receive_i_fr = Q170,             
          receive_i_fr_oth = Q170_13_TEXT,
@@ -41,8 +46,9 @@ clean_data <- clean_data %>%
          int_sought_affect = Q175,            
          vacc_status = Q179,             
          vacc_status_future = Q180,
-         age, gender, race, race_5_TEXT, hispanic, educ, income, employment) %>% 
-  
+         age, gender, race, race_5_TEXT, hispanic, educ, income, employment, zipcode,
+         duration) %>% 
+  left_join(zips, by = 'zipcode') %>% 
   # Clean up variable types 
   mutate(across(to_factor, as_factor),
          vacc_status = case_when(vacc_status == "Yes" ~ TRUE,
@@ -77,10 +83,10 @@ clean_data <- clean_data %>%
   
   # educ, cleaning
   mutate(college = case_when(educ %in% c('Graduate or professional degree', 
-                                         "Bachelor's degree",
-                                         "Associate's or Technical degree",
-                                         'Some college') ~ TRUE,
-                             educ %in% c('High school graduate', 
+                                         "Bachelor's degree") ~ TRUE,
+                             educ %in% c("Associate's or Technical degree",
+                                         'Some college',
+                                         'High school graduate', 
                                          "Less than high school") ~ FALSE)) %>% 
   
   # received information from,  cleaning
@@ -102,6 +108,7 @@ clean_data <- clean_data %>%
          across(int_sought_fr_pers:int_sought_fr_onlsearch, ~ replace_na(.x, FALSE))) %>% 
   
[…]

### 2022-01-23 paper2.Rmd
Finish Results

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra, scales)
+pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
+               # rms, 
+               modelsummary, showtext, thematic, kableExtra, scales)
 
@@
 ## Automatically use showtext to render text
-font_add_google("Open Sans", "open_sans")
+font_add_google("Lora", "lora")
 showtext_auto()
@@
       # Figure assembly
-      plot.title = element_text(family="open_sans",
+      plot.title = element_text(family="lora",
                                 size = rel(1), 
-                                face = "bold",
                                 margin = margin(0,0,5,0), 
@@
       plot.title.position = "plot",
-      plot.subtitle = element_text(family="open_sans",
+      plot.subtitle = element_text(family="lora",
                                    size = rel(0.85)),
-      plot.caption = element_text(family="open_sans",
+      plot.caption = element_text(family="lora",
                                   size = rel(0.70),
@@
       # Axes
-      axis.title = element_text(family="open_sans", 
-                                size = rel(0.85),
-                                face = "bold"),
-      axis.text = element_text(family="open_sans", 
-                               size = rel(0.70), 
-                               face = "bold"),
+      axis.title = element_text(family="lora", 
+                                size = rel(0.85)),
+      axis.text = element_text(family="lora", 
+                               size = rel(0.70)),
       axis.line = element_line(color = "black", 
@@
       # Legend
-      legend.title = element_text(family="open_sans",
-                                  size = rel(0.85), 
-                                  face = "bold"),
-      legend.text = element_text(family="open_sans", 
-                                 size = rel(0.70), 
-                                 face = "bold"),
+      legend.title = element_text(family="lora",
+                                  size = rel(0.85)),
+      legend.text = element_text(family="lora", 
+                                 size = rel(0.70)),
       legend.key = element_rect(fill = "transparent", 
@@
                                       color = "#17252D"),
-      strip.text = element_text(family="open_sans",
+      strip.text = element_text(family="lora",
                                 size = rel(0.85), 
-                                face = "bold", 
                                 color = "white", 
@@
 }
-
 print_perc <- function(var){
@@
 
-side_by_side <- function(models, ...) {
-    estimates <- c("Coef." = "{estimate}{stars}", 
-                       "Std.Error" = "({std.error})")
-    models <- rep(models, each = length(estimates))
-    estimates <- rep(estimates,
-                     times = length(models)/length(estimates))
-
-    alignment <- paste(rep('l', length(models) + 1), collapse = '')
-
-    names(models) <- names(estimates)
-
-    modelsummary(models = models, 
-                 estimate = estimates,
-                 statistic = NULL,
-                 align = alignment, ...)
-}
 ```
@@
 modern human life, it makes sense that performing online search has become one
-*f the most convenient vehicles for information search. While Small
+of the most convenient vehicles for information search. While Small
 [-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
@@
 information will have done so online.
+
+<!-- TODO add a hypothesis here -->
 
@@
 
-```{r desc-table-1}
+```{r table-1-desc}
 #| results = "asis"
@@
     (`Race, Asian or Pacific Islander` = race_asian) +
-    (`Some College, or above` = college)  ~ 
+    (`Associate's Deg or above` = college)  ~ 
     (Mean + SD) ,
@@
 
-```{r desc-table-2}
+```{r table-2-desc}
 #| results = "asis"
@@
 
-My analytic strategy proceeds in four steps. In Tables X & Y, I present descriptive
-statistics for all study variables, including variable ranges, means, and standard
-deviations.
+# Analysis
 
-In Table 3, I fit a model of state mobility scores using robust regression with the M estimator and iterated re-weighted least squares (IWLS) to downweight the influence of outliers (Jorgenson 2007; Venables and Ripley 2002).
-Model
-1 regresses state mobility scores on dummy variables for week. This model tests
-whether mobility scores vary across the 8-week study period. We use dummy variables for week to capture thresholds in the association between week and mobility.
-Model 2 adjusts for state religiosity, median age, percent black, the unemployment
-rate, population density, and the mobility lag. This model tests whether state religiosity is associated with state mobility scores net of state demographic characteristics
+My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
+& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
+variables, including variable ranges, means, and standard deviations. For this 
+paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
+fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
+, I fit a logistic regression model predicting
+whether someone sought information about Covid-19 using their sources of
+information ('Received info') as well as various demographic variables such as
+age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
+the relationship between the coefficients and information seeking.^[Figures in this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
+In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
+by modelling a series of logistic regressions that predict the 5 different
+avenues of seeking information about Covid-19: from another person, from a
+doctor, on an online forum, on a social networking site, or using an online
+search tool.
+Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
+relationship between information receiving and information seeking behaviors and
+the choice to get vaccinated against Covid-19 through a logistic regression
+model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then illustrates
+the relationship between the coefficients and vaccination outlook.
 
+# Results
 ```{r clean_before_reg}
@@
   'gender=Other' = 'Gender, Other',
-  'college1' = 'Some College +',
+  'college1' = "Associate's Deg or above",
   'race_white1' = 'White',
@@
 ```
-
-# What predicts someone intentionally searched for information
-
-Q171 And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.
-
-* Yes
-* No
-
-```{r model1-table}
+## Information Seeking
+```{r table-model-1}
 #| results = "asis"
@@
               college,
-            data = rain, family = binomial)
+            data = rain, family = binomial(link="logit"))
+nullmod1 <- glm(formula = int_sought ~ 1,
+            data = rain, family = binomial(link="logit"))
+psuedor2 <- as.numeric(1-(logLik(mod1)/logLik(nullmod1)))
 
-# library(patchwork)
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_pers") +
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_tv") + 
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup")
-
-# mod1 = list(mod1)
-
-# side_by_side(mod1, 
-#              gof_omit = 'AIC',
-#              title = 'What predicts someone intentionally searched for information',
-#             coef_map = regression_labels,
-#             notes = 'Exponentiated Coefficients',
-#             exponentiate = TRUE,
-#             output = "kableExtra") %>%
-#   kable_styling(latex_options = c("HOLD_position", "striped"))
+rows <- tribble(~term, ~model1,
+                "$R_{McFadden}^2$", psuedor2)
+attr(rows, 'position') <- c(14, 4)
 
@@
             title = 'What predicts someone intentionally searched for information',
+            add_rows = rows,
             coef_map = regression_labels,
-            notes = 'Exponentiated Coefficients',
+            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Exponentiated Coefficients'),         
             exponentiate = TRUE,
             output = "kableExtra") %>%
-  kable_styling(latex_options = c("HOLD_position", "striped"))
+  kable_styling(latex_options = c("hold_position", "striped"))
 
@@
 
-```{r model1-plot}
+```{r plot-model-1}
 #| fig.cap='Plot of Coefficients, Model 1'
@@
            robust = TRUE) +
-  labs(title = 'What predicts someone intentionally searched for information', caption = 'Coefficients Scaled and robust') +
-  theme_diss()
+  labs(title = 'What predicts someone intentionally searched for information',
+       caption = 'Exponentiated Coefficients: Scaled and Robust') +
+  ylab("") +
+  theme_diss() +
+  scale_color_manual(values = my_palette[3])
 ```
-\newpage
 
-# What is associated with using different kinds of search vehicles?
+Table \@ref(tab:table-model-1) provides the results of my logistic regression
+analysis predicting whether someone sought information about Covid-19. These
+initial results suggest similar results for each vehicle of information
+delivery: each mode of receiving information whether from a doctor, a person,
+the news, a social networking site, or an online forum, all increase the odds of
+seeking out information. For example, respondents who had received information 
+from a doctor or other medical professional were `r round(exp(mod1$coefficients[['receive_i_fr_dr1']]),2)`
+(relative odds ratio = $exp(\beta k)$, _p_ < 0.001) times more likely to seek
+out information over someone who hadn't. Similarly, respondents who had received 
+information from 'a person  like friend, neighbor, or family member that [they] know'
+were `r round(exp(mod1$coefficients[['receive_i_fr_pers1']]),2)`
+( _p_ < 0.001) times more likely to seek out information over someone who hadn't
+received information from a person like that. Interesting, those who had
+received information from an online discussion group, listserve, or other online
+forum including a Facebook group or subreddit were 
+`r round(exp(mod1$coefficients[['receive_i_fr_onlgroup1']]), 2)` ( _p_ < 0.001)
+times more likely to search out more information than someone who hadn't. While 
+most demographic variables don't seem to have a strong effect on whether someone
+sought out information about the Covid-19 vaccine, a few key variables had strong
+associations. Age, for instance, is associated with seeking information; every 
+additional year of age a person holds they are
+`r label_percent()(exp(mod1$coefficients[['age']])-1)` 
+more likely to search for information, possibly indicating a generational effect
+of information seeking patterns ( _p_ < 0.01). Additionally, those who were more 
+educated, that is those with an associate's degree or higher, were 
+`r round(exp(mod1$coefficients[['college1']]), 2)` 
+more likely to seek additional information than those without the degree 
+( _p_ < 0.05). And finally, there is evidence to suggest that the Black or 
+African American sample was more likely to seek out information, specifically: 
+Blacks were `r round(exp(mod1$coefficients[['race_black1']]), 2)` times more likely 
+to seek out information over non-Blacks ( _p_ < 0.05). Figure \@ref(fig:plot-model-1) illustrates
+the relationship between the coefficients and information seeking.
 
-```{r model2-table}
+## Information Search Vehicles
+```{r table-model-2}
 #| results = "asis"
@@
 part2_models <- list()
+
+part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
 
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial)
-
-part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial)
+         data = rain, family = binomial(link="logit"))
 
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial)
+         data = rain, family = binomial(link="logit"))
 
-part2_models[['Social Networking\nSite']] <- glm(formula = int_sought_fr_onlnet ~ 
+part2_models[['Social Networking Site']] <- glm(formula = int_sought_fr_onlnet ~ 
            receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial)
+         data = rain, family = binomial(link="logit"))
 
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial)
+         data = rain, family = binomial(link="logit"))
+
+moda <- glm(formula = int_sought_fr_dr ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_a <- as.numeric(1-(logLik(part2_models[['Doctor']])/logLik(moda)))
+
+modb <- glm(formula = int_sought_fr_pers ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_b <- as.numeric(1-(logLik(part2_models[['Person']])/logLik(modb)))
+
+modc <- glm(formula = int_sought_fr_onlgroup ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_c <- as.numeric(1-(logLik(part2_models[['Online Forum']])/logLik(modc)))
+
+modd <- glm(formula = int_sought_fr_onlnet ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_d <- as.numeric(1-(logLik(part2_models[['Social Networking Site']])/logLik(modd)))
+
+mode <- glm(formula = int_sought_fr_onlsearch ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_e <- as.numeric(1-(logLik(part2_models[['Online Search']])/logLik(mode)))
+
+rows <- tribble(~term, ~Doctor, ~Person, ~`Online Forum`, ~`Social Networking Site`, ~`Online Search`,
+                "$R_{McFadden}^2$", r2_a,   r2_b, r2_c, r2_d, r2_e)
+attr(rows, 'position') <- c(14, 9)
 
@@
             coef_map = regression_labels,
-            notes = 'Note: Exponentiated Coefficients',
+            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Exponentiated Coefficients'),            
             title = 'What predicts someone intentionally searched for information, by vehicle of information search',
             exponentiate = TRUE,
+            add_rows = rows,
             output = "kableExtra") %>%
-  kable_styling(latex_options = c("scale_down", "HOLD_position", "striped"))  %>%
+  kable_styling(latex_options = c("scale_down", "hold_position", "striped"))  %>%
   add_header_above(c(" " = 1, "Dependent Variable" = 5))
-
-# 
-# 
-# 
-# 
-# side_by_side(part2_models, 
-#              gof_omit = 'AIC',
-#             coef_map = regression_labels,
-#             notes = 'Note: Exponentiated Coefficients',
-#             title = 'What predicts someone intentionally searched for information, by vehicle of information search',
-#             exponentiate = TRUE,
-#             output = "kableExtra") %>%
-#   kable_styling(latex_options = c("HOLD_position", "striped")) %>% 
-#   add_header_above(c(" ", 
-#                      "Person" = 2,
-#                      "Doctor" = 2, 
-#                      "Online Forum" = 2,
-#                      "Social Networking\nSite" = 2,
-#                      "Online Search"  = 2)) %>%
-#   add_header_above(c(" " = 1, "Dependent Variable" = 10)) %>%
-#   kableExtra::landscape()
-
 ```
 
-\newpage
+To further investigate how people search for information, I asked those who had
+sought information out intentionally, "How did you look for information about
+the Covid-19 vaccine?" Results are displayed in Table \@ref(tab:table-model-2).
+Because respondents could select as many responses as applicable, each response
+is recorded as a dichotomous variable and modeling using logistic regression.
+Modeling each response as a separate formula is useful for interpretation, but
+there are important caveats: because each logistic regression is on a different
+scale, one must not compare the magnitude of coefficients between models. We
+can, however, use the direction and significance of the coefficients to draw
+conclusions about these different forms of information search vehicles.
 
-# Researching how you search for vaccination information affects vaccination status
-```{r model3-table}
+The first model predicts whether or not a respondent sought information
+intentionally about Covid-19 vaccinations by asking their doctor or another
+health professional. First and foremost, I find that those who received
+information about Covid-19 vaccinations were 
+`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_dr1']]), 2)` times
+more likely to seek out more information from their doctor than those who had 
+not ( _p_ < 0.001). However, receiving information from other vehicles also 
+increased the odds of seeking out information from medical professions. Those who
+received information from a person like a friend or a relative were 
+`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_pers1']]), 2)` times
+more likely to ask their doctor ( _p_ < 0.001), while those who received 
+information from the news or television were
+`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_tv1']]), 2)`
+times more likely ( _p_ < 0.01). I also find that those who received information
+from an online forum like a subreddit were 
+`r label_percent()(round(exp(part2_models$Doctor$coefficients[['receive_i_fr_onlgroup1']]), 2)-1)`
+more likely to ask their doctors than those who hadn't ( _p_ < 0.05). Finally, 
+respondents with an associate's degree or higher were 
+`r label_percent()(round(exp(part2_models$Doctor$coefficients[['college1']]), 2)-1)`
+more likely to ask their doctor for information on the Covid-19 vaccinations
+than those who held less education ( _p_ < 0.01).
+
+The second model predicts whether or not a respondent sought information about
+Covid-19 vaccinations by asking a person like friend, neighbor, or family member
+that they know. Only three coefficients in this model were significant and help
+us draw any conclusions on who is most likely to activate their personal social
+network for informational support. In this study, I find that receiving
+information about the vaccine from a doctor, their personal network, or a social
+networking site is associated with seeking out more information. Those who 
+received information from a doctor or other medical professional were 
+`r round(exp(part2_models$Person$coefficients[['receive_i_fr_dr1']]), 2)`
+times more likely to seek information from a person like a friend  ( _p_ < 0.001). 
+Moreover, it seems that receiving information from your personal social network,
+like a friend or relative, is associated with seeking information from those 
+same people; in fact, I find that those who did are 
+`r round(exp(part2_models$Person$coefficients[['receive_i_fr_pers1']]), 2)` more
+likely to do so ( _p_ < 0.001). Finally, the respondents who received information
+about the vaccine on a social networking site were 
+`r label_percent()(round(exp(part2_models$Person$coefficients[['receive_i_fr_onlnet1']]), 2)-1)`
+ more likely to seek information from their personal network than those who hadn't 
+( _p_ < 0.01). The unexpected result of this model is that very few factors predict
+personal social network activation and this model has the lowest McFadden's R^2, 
+indicating possible omitted variables.
+
+I also wanted to see what was associated with posting in an online discussion
+group, listserve, or other online forum like a Facebook Group or Subreddit about
+Covid-19 vaccinations. This is conceptually different that posting a query on a
+social networking site like Facebook or twitter where identities are involved,
+but is theoretically more [costly?][friction?] than searching on an internet
+search engine. I found that having received information about the vaccine from 
+your personal social network (like a friend or relative), the news, or an online
+forum was associated with higher odds of querying an online forum. Specifically,  
+receiving information from your personal network is associated with 
+`r round(exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_pers1']]), 2)`
+higher odds ( _p_ < 0.001), from news or television media with `r round(exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_tv1']]), 2)` higher odds ( _p_ < 0.05), and 
+receiving information on an online forum associated with 
+`r round(exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_onlgroup1']]), 2)`
+higher odds ( _p_ < 0.001). Moreover, I found that those with an associate's 
+degree or above were 
+`r round(exp(part2_models$'Online Forum'$coefficients[['college1']]), 2)` times
+more likely to search for information on an online forum ( _p_ < 0.001). Finally,
+I found a racial-ethnic with Hispanic-Latinos; I found that they were about 
+`r label_percent()(exp(part2_models$'Online Forum'$coefficients[['hispanic1']])-1)`
+more likely to query an online forum than non-Hispanics ( _p_ < 0.05). However, 
+there were also a few variables that lowered the odds of posting in an online 
+discussion group. First, those who had received information from a social 
+networking site were
+`r label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_onlnet1']]))` 
+less likely to query a forum than those who hadn't (relative odds ratio =
+$1 - exp(\beta k)$, _p_ < 0.01). Morever, I find more ethno-racial effects: 
+Respondents who claimed Asian ancestry were 
+`r label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['race_asian1']]))` 
+less likely to query online forum ( _p_ < 0.01).
+
+The fourth model predicts whether an individual sought information about 
+Covid-19 vaccinations through posted queries on a social networking site such 
+as Facebook timeline, Twitter status update, or Linkedin. Receiving information
+about Covid-19 seems to be quite related to posting on socia media. Those who 
+received information from their doctor's had 
+`r round(exp(part2_models$'Social Networking Site'$coefficients[['receive_i_fr_dr1']]), 2)`
+higher odds of posting on a social networking site ( _p_ < 0.01), while those 
+who received their information from tv/news had `r round(exp(part2_models$'Social Networking Site'$coefficients[['receive_i_fr_tv1']]), 2)` higher odds ( _p_ < 0.05). 
+Furthermore, those who received information on social networking sites were more 
+likely to post queries on social networking sites ($\beta$ = 
+`r round(exp(part2_models$'Social Networking Site'$coefficients[['receive_i_fr_onlnet1']]), 2)`,  _p_ < 0.001). 
+The respondents in our sample who received information on online forums had
+`r round(exp(part2_models$'Social Networking Site'$coefficients[['receive_i_fr_onlgroup1']]), 2)` 
+higher odds of posting queries on their social networking platforms ( _p_ < 0.001). 
+I found a relationship between education and posting on social networking sites
+as well; specifically, those with an Associate's degree or above were `r round(exp(part2_models$'Social Networking Site'$coefficients[['college1']]), 2)` times more likely to post vaccination 
+queries on social networking sites than those with lower education ( _p_ < 0.001).
+Finally, I find that Hispanic-Latinos were 
+`r label_percent()(exp(part2_models$'Social Networking Site'$coefficients[['hispanic1']])-1)`
+more likely to ask their connections on a social networking site about the 
+Covid-19 vaccinations than non-Hispanics ( _p_ < 0.01).
+
+Searching for information using an online search engine such as Google or Bing 
+is theorically the search vehicle with the least amount of social or cognitive 
+friction. Our descriptive statistics showed that not everyone used this vehicle,
+with only 41% of our sample (See Table \@ref(tab:table-1-desc)) having sought
+information about the Covid-19 vaccines using online search engines. My model
+reveals interesting patterns to help explain the variation. As with previous 
+models, receiving information of any kind increase the odds of online search, 
+though to varying magnitudes (Doctor:
+`r round(exp(part2_models$'Online Search'$coefficients[['receive_i_fr_dr1']]), 2)` odds; 
+Person:
+`r round(exp(part2_models$'Online Search'$coefficients[['receive_i_fr_pers1']]), 2)` odds; 
+News or Television: 
+`r round(exp(part2_models$'Online Search'$coefficients[['receive_i_fr_tv1']]), 2)` odds; 
+Social Networking Site:
+`r round(exp(part2_models$'Online Search'$coefficients[['receive_i_fr_onlnet1']]), 2)` odds; 
+Online Forum: 
+`r round(exp(part2_models$'Online Search'$coefficients[['receive_i_fr_onlgroup1']]), 2)` odds).
+I also find that older respondents were more likely to search online, with each 
+addition year aged to yield
+`r label_percent()(exp(part2_models$'Online Search'$coefficients[['age']])-1)`
+higher odds of searching online ( _p_ < 0.001). The most interesting variations
+come from what decreases the odds of online search. First, those with an
+Associate's degree or higher were 
+`r label_percent()(1-exp(part2_models$'Online Search'$coefficients[['college1']]))` 
+less likely to search online for questions about Covid-19 than those with less
+educational attainment ( _p_ < 0.001). In addition, I find that Hispanic-Latinos 
+had `r label_percent()(1-exp(part2_models$'Online Search'$coefficients[['hispanic1']]))` 
+lower odds of searching online than non-Hispanics ( _p_ < 0.05).
+
+## Vaccination Views
+
+```{r table-model-3}
 #| results = "asis"
@@
            college,  
-         data = rain, family = binomial)
+         data = rain, family = binomial(link="logit"))
 
-# 
-# mod3 = list(mod3)
-# 
-# 
-# side_by_side(mod3, 
-#              gof_omit = 'AIC',
-#             title = 'Does receiving or searching for information predict vaccination status?',
-#             notes = 'Note: Exponentiated Coefficients',
-#             coef_map = regression_labels,
-#             exponentiate = TRUE,
-#             output = "kableExtra") %>%
-#   kable_styling(latex_options = c("HOLD_position", "striped"))
-#
+nullmod3 <- glm(formula = vacc_view_pos ~ 1,
+            data = rain, family = binomial(link="logit"))
+psuedor2_mod3 <- as.numeric(1-(logLik(mod3)/logLik(nullmod3)))
+
+rows <- tribble(~term, ~model1,
+                "$R_{McFadden}^2$", psuedor2_mod3)
+attr(rows, 'position') <- c(19, 4)
 
@@
             title = 'Does receiving or searching for information predict vaccination status?',
-            notes = 'Note: Exponentiated Coefficients',
+            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Exponentiated Coefficients'),        
             coef_map = regression_labels,
+            add_rows = rows,
             exponentiate = TRUE,
             output = "kableExtra") %>%
-  kable_styling(latex_options = c("HOLD_position", "striped"))
+  kable_styling(latex_options = c("hold_position", "striped"))
 ```
+Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
+relationship between information receiving and information seeking behaviors and
+the choice to get vaccinated against Covid-19 through a logistic regression
+model predicting Vaccination Outlook. I find that receiving information from a
+doctor or other medical profession is associated with 
+`r round(exp(mod3$coefficients[['receive_i_fr_dr1']]), 2)` odds of receiving 
+a Covid-19 vaccinated ( _p_ < 0.001) and that seeking information from a doctor
+also increases the odds of vaccination by 
+`r round(exp(mod3$coefficients[['int_sought_fr_dr1']]), 2)` ( _p_ < 0.001).
+I find that my respondents who received information on a social networking site 
+like Facebook or Twitter about the vaccines were 
+`r label_percent()(1-round(exp(mod3$coefficients[['receive_i_fr_onlnet1']]), 2))` 
+**less likely** to get vaccinated than those who received no information through
+that vehicle ( _p_ < 0.001). However, I did find that those who reached out to
+family or friends with their concerns were 
+`r label_percent()(exp(mod3$coefficients[['int_sought_fr_pers1']])-1)` more likely
+to become vaccinated ( _p_ < 0.05). Furthermore, my respondents who held an 
+Associate's degree or above had `r round(exp(mod3$coefficients[['college1']]), 2)`
+higher odds of becoming immunized ( _p_ < 0.001). And finally, I found further
+ethno-racial differences in my sample. I found that Hispanic-Latinos had 
+`r round(exp(mod3$coefficients[['hispanic1']]), 2)` higher odds of vaccination
+than non-Hispanics ( _p_ < 0.05) and that my Asian sample had 
+`r round(exp(mod3$coefficients[['race_asian1']]), 2)` higher odds as well over
+non-Asians ( _p_ = 0.09). See Figure \@ref(fig:plot-model-3) for a visual 
+representation of how these different coefficients are related to vaccination 
+outlook. 
+<!-- TODO: watch out about saying vaccinated, this variable is about opinion -->
 
-```{r model3-plot}
+```{r plot-model-3}
 #| fig.cap='Plot of Coefficients, Model 3'
@@
   labs(title = 'Does receiving or searching for information predict vaccination sentiment?', 
-       caption = 'Coefficients Scaled and robust') +
-  theme_diss()
+       caption = 'Exponentiated Coefficients: Scaled and Robust') + 
+  ylab("") +
+  theme_diss()+
+  scale_color_manual(values = my_palette[3])
+```
 
-# library(patchwork)
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
-# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup") + 
-# sjPlot::plot_model(m, type = "pred", terms = "int_sought_fr_dr") +
-# sjPlot::plot_model(m, type = "pred", terms = "college") 
-```
+# Discussion
+
+summary of purpose
+
+for results - Table 1
+this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ...
+
+rather than on “the receiver as an active information seeker and processor."
+[@johnsonComprehensiveModelCancerRelated1993].
+
+Est velit egestas dui id ornare arcu odio ut. Tempus iaculis urna id volutpat
+lacus laoreet non curabitur gravida. Integer malesuada nunc vel risus commodo.
+Ipsum nunc aliquet bibendum enim facilisis gravida. Ac turpis egestas maecenas
+pharetra convallis posuere morbi leo. Id diam vel quam elementum pulvinar etiam.
+Neque aliquam vestibulum morbi blandit cursus risus at ultrices mi. Sem
+fringilla ut morbi tincidunt augue interdum velit euismod. Ullamcorper eget
+nulla facilisi etiam dignissim diam quis enim lobortis. Turpis egestas pretium
+aenean pharetra magna ac placerat vestibulum lectus. Elit ut aliquam purus sit
+amet luctus venenatis. Vitae tempus quam pellentesque nec nam. In est ante in
+nibh. Nisl tincidunt eget nullam non nisi est sit. Cras adipiscing enim eu
+turpis egestas. Velit dignissim sodales ut eu sem integer vitae justo eget. Arcu
+non sodales neque sodales ut etiam sit amet. Turpis in eu mi bibendum neque
+egestas congue quisque egestas.
+
+At varius vel pharetra vel turpis nunc eget lorem. In nulla posuere sollicitudin
+aliquam. Dui faucibus in ornare quam. Vivamus arcu felis bibendum ut tristique.
+Ornare aenean euismod elementum nisi. Eget aliquet nibh praesent tristique.
+Rhoncus dolor purus non enim praesent elementum. Id faucibus nisl tincidunt eget
+nullam non nisi est. Eget arcu dictum varius duis at consectetur lorem donec
+massa. At tempor commodo ullamcorper a lacus vestibulum sed arcu.
+
+Lectus mauris ultrices eros in. Diam ut venenatis tellus in metus vulputate eu
+scelerisque. Magna ac placerat vestibulum lectus mauris. Est velit egestas dui
+id ornare arcu odio ut. Sagittis aliquam malesuada bibendum arcu vitae
+elementum. Nisi lacus sed viverra tellus in hac habitasse. Nunc eget lorem dolor
+sed. Condimentum id venenatis a condimentum vitae. Ipsum faucibus vitae aliquet
+nec ullamcorper sit amet risus nullam. Tincidunt eget nullam non nisi est.
+Ornare quam viverra orci sagittis eu volutpat. Risus quis varius quam quisque.
+Lobortis scelerisque fermentum dui faucibus. A diam sollicitudin tempor id eu
+nisl nunc mi ipsum.
 

### 2022-01-24 paper2.Rmd
Add chi2 test

@@
 pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
-               # rms, 
                modelsummary, showtext, thematic, kableExtra, scales)
@@
 
+# Abstract 
+How do individuals perform information search, and what factors help them decide
+which information search vehicle to utilize, such as interpersonal networks or
+online tools, I investigate the above question  using individual survey data of
+934 Adults in the United States and find that
+
+Knowing that Google
+trends data only encompasses a small portion of the information-seeking done by
+modern humans, it is important to investigate what leads individuals to search
+for a question online using a search engine versus more traditional means of
+information gathering, such as network activation (asking someone in their
+social network for informational support). I predict that few people will
+activate their social network for informational support in my chosen case of
+Covid-19 vaccinations because of the social cost of doing so and that the
+majority will have utilized an online search engine.
+
 # Intro
@@
 In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
-by modelling a series of logistic regressions that predict the 5 different
-avenues of seeking information about Covid-19: from another person, from a
-doctor, on an online forum, on a social networking site, or using an online
-search tool.
+by investigating the difference in proportions of each of the vehicles in 
+\@ref(tab:model-2-chi2) and then by modelling a series of logistic regressions 
+that predict the 5 different avenues of seeking information about Covid-19: 
+from another person, from a doctor, on an online forum, on a social networking 
+site, or using an online search tool.
 Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
@@
             notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
-                      'Exponentiated Coefficients'),         
-            exponentiate = TRUE,
+                      'Raw, Unexponentiated Coefficients'),            
+            # exponentiate = TRUE,
             output = "kableExtra") %>%
@@
 ## Information Search Vehicles
+```{r model-2-chi2}
+#| results = "asis"
+
+chi <- rain %>% 
+  select(pers = int_sought_fr_pers,
+         dr = int_sought_fr_dr,
+         forum = int_sought_fr_onlgroup,
+         net = int_sought_fr_onlnet,
+         search = int_sought_fr_onlsearch)
+
+find_p <- function(x, y){
+  tab <- table(x, y)
+  as.numeric(chisq.test(tab)["p.value"])
+}
+
+chi_squared_tests <- 
+tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Online Network`, ~`Online Search`,
+'Person',   NA, find_p(chi$pers, chi$dr), find_p(chi$pers, chi$forum), find_p(chi$pers, chi$net), find_p(chi$pers, chi$search),
+'Dr',     NA, NA, find_p(chi$dr, chi$forum), find_p(chi$dr, chi$net), find_p(chi$dr, chi$search),
+'Online Forum',  NA, NA, NA, find_p(chi$forum, chi$net), find_p(chi$forum, chi$search),
+'Online Network',    NA, NA,NA, NA, find_p(chi$net, chi$search),
+'Online Search', NA, NA, NA, NA, NA)
+
+chi_squared_tests %>%
+  mutate(across(where(is.numeric), ~ sprintf("%.3f", round(., digits = 3)))) %>% 
+  mutate(Person = cell_spec(Person, format = "html", bold = Person < 0.05),
+       Dr = cell_spec(Dr, format = "html", bold = Dr < 0.05),
+       `Online Forum` = cell_spec(`Online Forum`, format = "html", bold = `Online Forum` < 0.05),
+       `Online Network` = cell_spec(`Online Network`, format = "html", bold = `Online Network` < 0.05),
+       `Online Search` = cell_spec(`Online Search`, format = "html", bold = `Online Search` < 0.05)) %>% 
+  kable(., escape = FALSE,
+      digits=3,  
+      caption = "Pearson's $\\chi^2$ test with Yates' continuity
+	correction  between each Information Search Vehicle",
+      col.names = c("",'Person', 'Dr', 'Online Forum', 'Online Network', 'Online Search')      ) %>% 
+  kable_styling(latex_options = c("hold_position", "striped"),
+                full_width = F) %>%
+  column_spec(column = 1, bold = T) %>% 
+  footnote(c("Bolded values are significant using $\\alpha = 0.05$, two-tailed test"))
+```
+
 ```{r table-model-2}
@@
             notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
-                      'Exponentiated Coefficients'),            
+                      'Raw, Unexponentiated Coefficients'),            
             title = 'What predicts someone intentionally searched for information, by vehicle of information search',
-            exponentiate = TRUE,
+            # exponentiate = TRUE,
             add_rows = rows,
@@
 conclusions about these different forms of information search vehicles.
+
+TODO interpret table \@ref(tab:model-2-chi2), the chi2 tests to see differences
 
@@
             notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
-                      'Exponentiated Coefficients'),        
+                      'Raw, Unexponentiated Coefficients'),            
             coef_map = regression_labels,
             add_rows = rows,
-            exponentiate = TRUE,
+            # exponentiate = TRUE,
             output = "kableExtra") %>%
@@
 
-summary of purpose
-
-for results - Table 1
-this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ...
+summary of purpose of paper
+
+We contribute to the literature by using a multivariable approach to identify
+the sociodemographic factors associated with specific panethnic label
+preferences among Latinos/Hispanics. Specifically, we focus on how U.S. region,
+generation-since-immigration, racial identification, citizenship status,
+language use, national origin, education, and political affiliation shape
+panethnic label preference. We also call attention to factors associated with no
+preference at all for these terms
+
+table 1 and 2 main findings
+
+- receive info from any source increases searching for information 
+- older respondents more likely to search for information, perhaps indicating that 
+they are less likely to trust initial sources and dig deeper, perhaps indicating less
+polarization among older groups? 
+- higher education more likely to seek out  more information, also seen in table 2
+- blacks more likely to seek out more information
+usage of different information search vehicles varies by demographics and also reception of different ifnromation
+- overall, receiving information about Covid-19 vaccination generally spurs information seeking behaviors, though there are variations
+- receive info from doctor leads to searching info from doctor, likely indicates good communication and trust in doctor, solid relationship with healthcare professionals
+- few things predict seeking out information from another person, personal networks are so embedded in everyday life so perhaps don't remember doing it or behavioral prediction is notoriously hard
+- Received Info, Social Networking Site negatively predicts Online Forum, indicating that if your social networks fulfill your need for information you don't need to extend out to online forums to ask for things, need is already met?
+- Asians are really unlikely to use online forums to find information in this context, very strong association but hispanics are more likely than non-hispanics to search online 
+- online search is much less likely from those with higher education, which is counter intuitive since they are the population that has been the most trained in research methods and critical thinking ..
+perhaps they trust the information that they hear if they consider it to be a trusted source (typical higher education format of trust the professor) so they don't look deeper into it?
+basically already have high social capital in other ways, already set up to receive the information they needed and trusted
+- older populations are more likely to 'just google it'
+
+takeaways: Not everyone is activating their personal social networks or using Google in the same rates, the internal variation of users is important to consider when using something like Google Trends
+education really affects information seeking behavior
+ethno-racial differences affect information seeking behavior, more research should look into why there are group differences (likely cultural)
+
+Takeaway 2: in person, online, or search engines?
+
+table 3 main findings 
+- very important for getting people to get vaccinated - a major goal for public Health authorities over the last two years
+- extremely importnat given misinformation around vaccinations 
+- receiving information from a doctor or other medical profession (or seeking) leads to more positive opinions.
+action inspired by this - difficult because of lack of primary care doctors for many americans, but every doctor should discuss the importance for every patient they interact with
+- receiving information from a social networking site NOT an online for results in less vaccinations. 
+- differences in education level and race ; seen in prior literature however most current literature claims that anti-vacination attitudes span social class, political ideology, and X.
+
+social netwokring site
+info from doctor
+
+<!-- this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ...
+<--- I wish I knew what I was talking about here -->
 
@@
 pharetra convallis posuere morbi leo. Id diam vel quam elementum pulvinar etiam.
-Neque aliquam vestibulum morbi blandit cursus risus at ultrices mi. Sem
-fringilla ut morbi tincidunt augue interdum velit euismod. Ullamcorper eget
-nulla facilisi etiam dignissim diam quis enim lobortis. Turpis egestas pretium
-aenean pharetra magna ac placerat vestibulum lectus. Elit ut aliquam purus sit
-amet luctus venenatis. Vitae tempus quam pellentesque nec nam. In est ante in
-nibh. Nisl tincidunt eget nullam non nisi est sit. Cras adipiscing enim eu
-turpis egestas. Velit dignissim sodales ut eu sem integer vitae justo eget. Arcu
-non sodales neque sodales ut etiam sit amet. Turpis in eu mi bibendum neque
-egestas congue quisque egestas.
-
-At varius vel pharetra vel turpis nunc eget lorem. In nulla posuere sollicitudin
-aliquam. Dui faucibus in ornare quam. Vivamus arcu felis bibendum ut tristique.
-Ornare aenean euismod elementum nisi. Eget aliquet nibh praesent tristique.
-Rhoncus dolor purus non enim praesent elementum. Id faucibus nisl tincidunt eget
-nullam non nisi est. Eget arcu dictum varius duis at consectetur lorem donec
-massa. At tempor commodo ullamcorper a lacus vestibulum sed arcu.
-
-Lectus mauris ultrices eros in. Diam ut venenatis tellus in metus vulputate eu
-scelerisque. Magna ac placerat vestibulum lectus mauris. Est velit egestas dui
-id ornare arcu odio ut. Sagittis aliquam malesuada bibendum arcu vitae
-elementum. Nisi lacus sed viverra tellus in hac habitasse. Nunc eget lorem dolor
-sed. Condimentum id venenatis a condimentum vitae. Ipsum faucibus vitae aliquet
-nec ullamcorper sit amet risus nullam. Tincidunt eget nullam non nisi est.
-Ornare quam viverra orci sagittis eu volutpat. Risus quis varius quam quisque.
-Lobortis scelerisque fermentum dui faucibus. A diam sollicitudin tempor id eu
-nisl nunc mi ipsum.
 
 \newpage
+
+# Conclusion
+
 # References {-}

### 2022-01-24 paper2.Rmd
change chi2 to phi coefficient

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
+pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
                modelsummary, showtext, thematic, kableExtra, scales)
@@
 online tools, I investigate the above question using individual survey data of
-934 Adults in the United States and find that
-
-Knowing that Google
-trends data only encompasses a small portion of the information-seeking done by
-modern humans, it is important to investigate what leads individuals to search
-for a question online using a search engine versus more traditional means of
-information gathering, such as network activation (asking someone in their
-social network for informational support). I predict that few people will
+934 Adults in the United States and find that X and Y. Furthermore, this paper
+demonstrates that searching for a question online using a search engine or
+social network was more common than traditional means of information gathering,
+such as network activation (asking someone in their social network for
+informational support). Using X and Y theory I predict that that few people will
 activate their social network for informational support in my chosen case of
-Covid-19 vaccinations because of the social cost of doing so and that the
-majority will have utilized an online search engine.
+Covid-19 vaccinations because of the social cost of doing so but fail to find
+evidence for this thesis. I also investigate which information channels are
+associated with vaccinations against the virus, and find that social netwokring
+sites are associated with lower rates. I also find important ethnocracial
+differences in information search vehicles utilization and vaccination
+reception.
+
+<!-- TODO this needs a lot of work but its a start -->
 
@@
 
-## section B: Research Questions
+Research Questions
+
 * How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
@@
 age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
-the relationship between the coefficients and information seeking.^[Figures in this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
-In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
-by investigating the difference in proportions of each of the vehicles in 
-\@ref(tab:model-2-chi2) and then by modelling a series of logistic regressions 
-that predict the 5 different avenues of seeking information about Covid-19: 
-from another person, from a doctor, on an online forum, on a social networking 
-site, or using an online search tool.
+the relationship between the coefficients and information seeking.^[Figures in 
+this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
+In Table \@ref(tab:model-2-phi) I disaggregate information seeking behaviors by
+investigating the difference in proportions of each of the 5 different avenues
+of seeking information about Covid-19: from another person, from a doctor, on an
+online forum, on a social networking site, or using an online search tool. I
+investigate these differences through a phi coefficient [@warrens08], otherwise
+known as a mean square contingency coefficient which is used to investigate the
+degree of association between two binary variables. ^[To calculate the Phi
+Coefficient, I utilize the Psych `r` package [@psych] ] I then investiage the
+associations between my predictors and the 5 information search vehicles by
+modelling a series of logistic regressions in Table \@ref(tab:table-model-2).
 Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
@@
 the choice to get vaccinated against Covid-19 through a logistic regression
-model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then illustrates
-the relationship between the coefficients and vaccination outlook.
+model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then
+illustrates the relationship between the coefficients and vaccination outlook.
 
@@
 ## Information Search Vehicles
-```{r model-2-chi2}
-#| results = "asis"
-
-chi <- rain %>% 
+
+```{r model-2-phi}
+phi <- rain %>% 
   select(pers = int_sought_fr_pers,
@@
 
-find_p <- function(x, y){
+find_phi <- function(x, y){
   tab <- table(x, y)
-  as.numeric(chisq.test(tab)["p.value"])
+  phi(tab, digits = 3)
 }
 
-chi_squared_tests <- 
-tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Online Network`, ~`Online Search`,
-'Person',   NA, find_p(chi$pers, chi$dr), find_p(chi$pers, chi$forum), find_p(chi$pers, chi$net), find_p(chi$pers, chi$search),
-'Dr',     NA, NA, find_p(chi$dr, chi$forum), find_p(chi$dr, chi$net), find_p(chi$dr, chi$search),
-'Online Forum',  NA, NA, NA, find_p(chi$forum, chi$net), find_p(chi$forum, chi$search),
-'Online Network',    NA, NA,NA, NA, find_p(chi$net, chi$search),
+phi_squared_tests <- 
+  tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Social Networking Site`, ~`Online Search`,
+          'Person',   NA_complex_, find_phi(phi$pers, phi$dr), find_phi(phi$pers, phi$forum), find_phi(phi$pers, phi$net), find_phi(phi$pers, phi$search),
+          'Dr',     NA, NA, find_phi(phi$dr, phi$forum), find_phi(phi$dr, phi$net), find_phi(phi$dr, phi$search),
+          'Online Forum',  NA, NA, NA, find_phi(phi$forum, phi$net), find_phi(phi$forum, phi$search),
+          'Social Networking Site',    NA, NA,NA, NA, find_phi(phi$net, phi$search),
           'Online Search', NA, NA, NA, NA, NA)
 
-chi_squared_tests %>%
-  mutate(across(where(is.numeric), ~ sprintf("%.3f", round(., digits = 3)))) %>% 
-  mutate(Person = cell_spec(Person, format = "html", bold = Person < 0.05),
-       Dr = cell_spec(Dr, format = "html", bold = Dr < 0.05),
-       `Online Forum` = cell_spec(`Online Forum`, format = "html", bold = `Online Forum` < 0.05),
-       `Online Network` = cell_spec(`Online Network`, format = "html", bold = `Online Network` < 0.05),
-       `Online Search` = cell_spec(`Online Search`, format = "html", bold = `Online Search` < 0.05)) %>% 
-  kable(., escape = FALSE,
-      digits=3,  
-      caption = "Pearson's $\\chi^2$ test with Yates' continuity
-	correction  between each Information Search Vehicle",
-      col.names = c("",'Person', 'Dr', 'Online Forum', 'Online Network', 'Online Search')      ) %>% 
+kable(phi_squared_tests, digits=3,  
+      caption = "Phi Coefficient ($\\phi$) of binary association between each Information Search Vehicle",
+      col.names = c("",'Person', 'Dr', 'Online Forum', 'Social Networking Site', 'Online Search')) %>% 
   kable_styling(latex_options = c("hold_position", "striped"),
-                full_width = F) %>%
-  column_spec(column = 1, bold = T) %>% 
-  footnote(c("Bolded values are significant using $\\alpha = 0.05$, two-tailed test"))
+                full_width = F)
+
 ```
@@
 sought information out intentionally, "How did you look for information about
-the Covid-19 vaccine?" Results are displayed in Table \@ref(tab:table-model-2).
-Because respondents could select as many responses as applicable, each response
-is recorded as a dichotomous variable and modeling using logistic regression.
+the Covid-19 vaccine?" Because respondents could select as many responses as
+applicable, each response is recorded as a dichotomous variable. I first
+investigate how each Information Search Vehicle are related to each other using
+the Phi Coefficient ($\\phi$) of binary association between each Information
+Search Vehicle pair. The Phi coefficient can be interpreted like a correlation
+coefficient, with numbers closer to -1 or positive one indicating a very strong
+relationship [@warrens08]. Table \@ref(tab:model-2-chi2) shows the results of
+these coefficients. Out of the five information search vehicles investigated,
+there is evidence that the vehicles are distinctly different concepts because
+most coefficients fall under 0.3, the general rule of thumb for correlation 
+coefficients to indicate a relationship. There does seem to be a relationship
+between Online Forums and Social Networking Sites, possibly due to an
+individual's propensity to use online networks over in-person networks. These
+coefficients indicate a weak relationship between any two vehicles of
+information search and and that respondents in my sample utilize each of these a
+little bit differently.
+
+Results of each logistic regression are displayed in Table \@ref(tab:table-model-2).
 Modeling each response as a separate formula is useful for interpretation, but
@@
 
-TODO interpret table \@ref(tab:model-2-chi2), the chi2 tests to see differences
-
-The first model predicts whether or not a respondent sought information
-intentionally about Covid-19 vaccinations by asking their doctor or another
-health professional. First and foremost, I find that those who received
-information about Covid-19 vaccinations were 
+The first model in Table \@ref(tab:table-model-2) predicts whether or not a
+respondent sought information intentionally about Covid-19 vaccinations by
+asking their doctor or another health professional. First and foremost, I find
+that those who received information about Covid-19 vaccinations were
 `r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_dr1']]), 2)` times

### 2022-01-24 paper2.Rmd
Table 1 findings written

@@
 <!-- TODO this needs a lot of work but its a start -->
+Previous research has greatly failed to distinguish between the activation of
+information seeking behaviors online and offline. In this paper, I aim to
+uncover just how different various methods of information search are and begin a
+line of research inquiry that investigates the factors associated with each vehicle. 
+Finally, I also aimed to uncover how the different fountains of information and
+information search vehicles hold real world consequences through their associations
+with Covid-19 vaccination rates and intentions.
 
@@
 
-```{r table-model-2}
-#| results = "asis"
-
-part2_models <- list()
-
-part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
-
-part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
-
-part2_models[['Online Forum']] <- glm(formula = int_sought_fr_onlgroup ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
-
-part2_models[['Social Networking Site']] <- glm(formula = int_sought_fr_onlnet ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
-
-part2_models[['Online Search']] <- glm(formula = int_sought_fr_onlsearch ~ 
-           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
-           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
-           age + gender + college +
-           race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
-
-moda <- glm(formula = int_sought_fr_dr ~ 1,
-            data = rain, family = binomial(link="logit"))
-r2_a <- as.numeric(1-(logLik(part2_models[['Doctor']])/logLik(moda)))
-
-modb <- glm(formula = int_sought_fr_pers ~ 1,
-            data = rain, family = binomial(link="logit"))
-r2_b <- as.numeric(1-(logLik(part2_models[['Person']])/logLik(modb)))
-
-modc <- glm(formula = int_sought_fr_onlgroup ~ 1,
-            data = rain, family = binomial(link="logit"))
-r2_c <- as.numeric(1-(logLik(part2_models[['Online Forum']])/logLik(modc)))
-
-modd <- glm(formula = int_sought_fr_onlnet ~ 1,
-            data = rain, family = binomial(link="logit"))
-r2_d <- as.numeric(1-(logLik(part2_models[['Social Networking Site']])/logLik(modd)))
-
-mode <- glm(formula = int_sought_fr_onlsearch ~ 1,
-            data = rain, family = binomial(link="logit"))
-r2_e <- as.numeric(1-(logLik(part2_models[['Online Search']])/logLik(mode)))
-
-rows <- tribble(~term, ~Doctor, ~Person, ~`Online Forum`, ~`Social Networking Site`, ~`Online Search`,
-                "$R_{McFadden}^2$", r2_a,   r2_b, r2_c, r2_d, r2_e)
-attr(rows, 'position') <- c(14, 9)
-
-modelsummary(part2_models,
-             align="llllll",
-             statistic = NULL,
-            estimate = "{estimate}{stars}",
-            gof_omit = 'AIC',
-            coef_map = regression_labels,
-            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
-                      'Raw, Unexponentiated Coefficients'),            
-            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
-            # exponentiate = TRUE,
-            add_rows = rows,
-            output = "kableExtra") %>%
-  kable_styling(latex_options = c("scale_down", "hold_position", "striped"))  %>%
-  add_header_above(c(" " = 1, "Dependent Variable" = 5))
-```
-
 To further investigate how people search for information, I asked those who had
@@
 little bit differently.
+
+```{r table-model-2}
+#| results = "asis"
+
+part2_models <- list()
+
+part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
+
+part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
+
+part2_models[['Online Forum']] <- glm(formula = int_sought_fr_onlgroup ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
+
+part2_models[['Social Networking Site']] <- glm(formula = int_sought_fr_onlnet ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
+
+part2_models[['Online Search']] <- glm(formula = int_sought_fr_onlsearch ~ 
+           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
+           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
+           age + gender + college +
+           race_white + race_black + race_nat + race_asian + hispanic,  
+         data = rain, family = binomial(link="logit"))
+
+moda <- glm(formula = int_sought_fr_dr ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_a <- as.numeric(1-(logLik(part2_models[['Doctor']])/logLik(moda)))
+
+modb <- glm(formula = int_sought_fr_pers ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_b <- as.numeric(1-(logLik(part2_models[['Person']])/logLik(modb)))
+
+modc <- glm(formula = int_sought_fr_onlgroup ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_c <- as.numeric(1-(logLik(part2_models[['Online Forum']])/logLik(modc)))
+
+modd <- glm(formula = int_sought_fr_onlnet ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_d <- as.numeric(1-(logLik(part2_models[['Social Networking Site']])/logLik(modd)))
+
+mode <- glm(formula = int_sought_fr_onlsearch ~ 1,
+            data = rain, family = binomial(link="logit"))
+r2_e <- as.numeric(1-(logLik(part2_models[['Online Search']])/logLik(mode)))
+
+rows <- tribble(~term, ~Doctor, ~Person, ~`Online Forum`, ~`Social Networking Site`, ~`Online Search`,
+                "$R_{McFadden}^2$", r2_a,   r2_b, r2_c, r2_d, r2_e)
+attr(rows, 'position') <- c(14, 9)
+
+modelsummary(part2_models,
+             align="llllll",
+             statistic = NULL,
+            estimate = "{estimate}{stars}",
+            gof_omit = 'AIC',
+            coef_map = regression_labels,
+            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Raw, Unexponentiated Coefficients'),            
+            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
+            # exponentiate = TRUE,
+            add_rows = rows,
+            output = "kableExtra") %>%
+  kable_styling(latex_options = c("scale_down", "hold_position", "striped"))  %>%
+  add_header_above(c(" " = 1, "Dependent Variable" = 5))
+```
 
@@
 # Discussion
-
-summary of purpose of paper
-
-We contribute to the literature by using a multivariable approach to identify
-the sociodemographic factors associated with specific panethnic label
-preferences among Latinos/Hispanics. Specifically, we focus on how U.S. region,
-generation-since-immigration, racial identification, citizenship status,
-language use, national origin, education, and political affiliation shape
-panethnic label preference. We also call attention to factors associated with no
-preference at all for these terms
-
-table 1 and 2 main findings
-
-- receive info from any source increases searching for information 
-- older respondents more likely to search for information, perhaps indicating that 
-they are less likely to trust initial sources and dig deeper, perhaps indicating less
-polarization among older groups? 
-- higher education more likely to seek out  more information, also seen in table 2
-- blacks more likely to seek out more information
+Previous research in Sociology and Infodemiology has greatly failed to
+distinguish between the activation of information seeking behaviors online and
+offline. In this paper, I aim to uncover just how different various methods of
+information search are and begin a line of research inquiry that investigates
+the factors associated with each different vehicle. Finally, I also aimed to
+uncover how the different fountains of information and information search
+vehicles hold real world consequences through their associations with Covid-19
+vaccination rates and intentions.
+
+I first find that receiving information about Covid-19 vaccinations from any
+outlined source increases the likelihood of searching out more information. I
+also find important demographic differences in the overall propensity to seek
+out information. First, I find that the older a respondent is, the more likely
+they are to seek out information about Covid-19 vaccinations, possibly
+indicating [???? TODO]. Furthermore, I find that those who are more educated,
+that is my respondents who hold an Associate's degree or higher were more likely
+to seek out information; for the most part this trend can be observed in Table
+\@ref(tab:table-model-2) as well. Human Capital Theory [@mirowsky_ross98] may
+help to explain this finding; this theory claims that education helps
+individuals gaining health-related knowledge and use this knowledge to be
+proactive in their own lives. Finally, I find that my respondents who identified
+as Black were more likely to seek out further information; this may be explained
+by the maltreatment that African-Americans have endured in the US
+healthcare system [@baileyStructuralRacismHealth2017] which has led to major
+distrust of the medical establishment among the population [@center2019a; @murray15].
+
+(May need to cite [@bronson2014don] above or elsewhere)
+
+table 2 main findings
+
 usage of different information search vehicles varies by demographics and also reception of different ifnromation
@@
 # Conclusion
+Previous research has greatly failed to distinguish between the activation of
+information seeking behaviors online and offline. In this paper, I aim to
+uncover just how different various methods of information search are and begin a
+line of research inquiry that investigates the factors associated with each vehicle. 
+Finally, I also aimed to uncover how the different fountains of information and
+information search vehicles hold real world consequences through their associations
+with Covid-19 vaccination rates and intentions.
 

### 2022-01-24 paper2.Rmd
adding to front half

@@
 # Intro
-It is unclear how individuals choose to search for information through the
-multimedia environment of the 21st century. Much of the research conducted in
-social networks and communication focus on senders, influencers, and persuasion
-strategies [@mertonManifestLatentFunctions1968] rather than on “the receiver as
-an active information seeker and processor."
-[@johnsonComprehensiveModelCancerRelated1993].
+
+Information is all around us and permeates every facet of human society, from
+the hordes of data gathered during the internet age or passing gossip between
+friends. Human communication and human society are based on the circulation of
+information and knowledge. Information can be shared by others through
+information campaigns and consumed by an individual, called information push, or
+intentionally sought out by individuals, called information pull 
+[@cybenkoFoundationsInformationPush1999].
+
+Information is especially important given the prominent trends of
+misinformation, disinformation, and mistrust in traditional institutions
+[@starbird19; @kata10]. While no belief in false information can be thought of as
+harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
+have major ramifications for both the individual and the social world that
+surrounds them. For example, a new found public resistance to vaccination
+against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
+worldwide in 2019. This increase killed  142,000 people, most of whom were
+children under the age of five [@givetash19]. However, even in the ever-evolving
+research agenda of misinformation, much of the research focuses on spaces where
+individual first come into contact with conspiracy theories or other information
+rather than what individuals do with the information they obtain
+[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20]. 
+<!-- cite something else here -->
+
+The lack of research in this area makes it quite unclear how individuals choose
+to search for information through the multimedia environment of the 21st
+century. Even outside of the misinformation literature, much of the research
+conducted in social networks and communication focus on senders, influencers,
+and persuasion strategies [@mertonManifestLatentFunctions1968;
+@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
+“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993].
+
+<!-- TODO cleanup -->
+For this paper, I will use the case of Covid-19 vaccinations to explore the
+variation among information search vehicles. T
+
+Research Questions
+
+* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
+* What factors lead people to perform health information search online versus among social network ties? 
+* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?
+
+<!-- TODO  cleanup -->
+
+## subheading - how people search
+
+Active directed searching by individuals to obtain information is sparsely
+discussed in the sociological literature. Pejtersen
+[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
+information science, theorized that there are 5 strategies for searching for
+information. The most common strategy is browsing, where people follow leads
+based on associations without planning ahead. Another strategy is analytical,
+which includes an explicit consideration of all facets of the question to guide
+a search. The empirical method guides the search based on tactics that were
+successful in past research. The known site strategy is to go to the direct
+source of the information if known. And finally, the similarity method is to
+find information based on another similar question that already has an answer.
+These 5 strategies vary in their demands for prior knowledge, cognitive
+processing, memory, and time spent. While this theory is aimed at finding
+information in a library setting, scholars have extended the theory to other
+fields and validated the framework [@fidelHumanInformationInteraction2012]; the
+frame is a useful beginning point for my theories of information search through
+network activation or through computer-mediated communication.
+
+Some communication theorists ask why an answer to a question is sought in the
+first place. The Theory of Uncertainty Management
+[@brashersCommunicationUncertaintyManagement2001] professes that people search
+for information when their uncertainty around the subject leads to anxiety or
+other cognitive harms. The Theory of Motivated Information Management
+[@afifiTheoryMotivatedInformation2004; @afifiSeekingInformationSexual2006]
+extends the prior by adding that uncertainty itself is not the catalyst for
+information-search; rather, it is driven by a discrepancy between the current
+level of uncertainty on a subject and desired level of uncertainty.
+
+One way to find information is to activate network ties to find out information
+through a form of social support. Social support, while previously used
+interchangeably with the term social networks and social integration
+[@houseStructuresProcessesSocial1988], are the emotional, informational, and
+instrumental assistance functions performed between social ties and have strong
+and measurable association with health outcomes
+[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
+Informational support is the process of seeking “help in defining,
+understanding, and coping with problematic events and include education, advice,
+or referral to another source of support” [@winemiller_etal93, p. 640].
+Brashers, a health communications researcher, defines informational support
+slightly differently, focusing on the exchange of information that “facilitates
+coping with life stresses… that may be exchanged among members of a support
+network” [-@brashersInformationSeekingAvoiding2002, p. 260] <!--  Both of these
+definitions provide important lenses for my question of how computer-mediated or
+interpersonal information-seeking strategies vary.--> If information is needed
+but there is no search for coping or deeper understanding of important matters,
+people are likely to choose to search online.
 
@@
 education, advice, or referral to another source of  support”
-[@winemillerMeasurementStrategiesSocial1993, p. 640].
+[@winemiller_etal93, p. 640].
 
@@
 
+From studies of mass communication, uses and gratifications theory (UGT)
+[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985] may also
+lend itself to theorizing why computer-mediated or interpersonal
+information-seeking strategies vary. UGT posits that users are not passive
+consumers of media and that people have an active role in choosing different
+sources of media based on their satisfaction of specific needs on an individual
+basis. UGT is based on Maslow’s [-@maslowTheoryHumanMotivation1943] hierarchy of
+needs and is compatible with Lazarsfeld and Katz’s theory of two-step flow
+[-@katzPersonalInfluencePart1955] because people can choose their media and the
+opinion leaders they follow. Modern-day theorists have extended UGT theory and
+classified the uses and gratifications of the internet and of social media.
+Stafford, Stafford, and Schkade [-@staffordDeterminingUsesGratifications2004]
+theorize that the internet provides gratification through useful content that
+meets expectations, gratification from purposeful navigating or random browsing
+as a process, and social gratification from forming and deepening social ties.
+Leung [-@leungGenerationalDifferencesContent2013] theorizes that social media is
+gratifying for users because it allows for venting of negative feelings,
+provides recognition, provides entertainment, promotes social affection, and
+fulfills cognitive needs. Adapting UGT to my own purposes, I theorize that
+informational support will be activated from network ties when the informational
+need is related to forming and deepening social ties but search will be
+conducted online when information is needed but an individual does not have an
+additional cognitive need to fill through social interaction. Alternative goals
+such as identity management or relational maintenance
+[@brashersInformationSeekingAvoiding2002] need to be balanced and will determine
+where search is conducted.
+
+<!-- connect above and below paragraph to flow together -->
+<!-- TODO  cleanup -->
+
 As online search or interaction also allows increased anonymity, no or lowered
@@
 
-<!-- TODO add a hypothesis here -->
-
-For this paper, I will use the case of Covid-19 vaccinations to explore the
-variation among information search vehicles. There are theoretical reasons why
-individuals would choose to search for information among their network ties
-instead of online search. For instance, Rains
-[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
+there are theoretical reasons why individuals would choose to search for
+information among their network ties instead of online search. For instance,
+Rains [-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
 technical information about an illness online but turn to their social network
@@
 
-This research project is important because the vehicles used to search by people
-impacts the information they are exposed to. Given the large swaths of both
-misinformation and disinformation regarding Covid-19 [@mottaHowRightLeaningMedia2020; @pathakInfodemicsCOVID19Role2020; @shahsavariConspiracyTimeCorona2020] and
-the measurable impacts this misinformation has had on pandemic-related health
-behaviors, how we choose to search for information affects our own lives and the
-lives of others. Moreover, individuals who do not utilize social networks for
-information search may feel like they have no network support, leading to
-feelings of network isolation with major implications for mental health 
-[@thoitsMechanismsLinkingSocial2011]
-
-Research Questions
-
-* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
-* What factors lead people to perform health information search online versus among social network ties? 
-* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?
+<!-- TODO add a hypothesis here -->
 
@@
 participants were paid and recruited using Amazon Turk (MTurk). The total valid
-survey responses (n = `r nrow(rain)`) were selected from a total of 1,066
+survey responses (_n_ = `r nrow(rain)`) were selected from a total of 1,066
 respondents; some responses were disqualified due to a few factors such as
@@
 Science and the Russell Sage Foundation. The main portion of this survey
-replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expandingon
+replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expanding on
 Small’s finding that people draw on much broader sources than “important people”
@@
 
-\newpage
-
 # Conclusion
@@
 with Covid-19 vaccination rates and intentions.
+
+The vaccines against the COVID-19 coronavirus prevent severe illness,
+hospitalization, and death. However, as I’m writing this, less than 55% of
+Arizonans over 12 years old are fully vaccinated against the virus. We know that
+people exposed to misinformation are much less likely to receive vaccinations
+against the virus [@loombaMeasuringImpactCOVID192021]. It is not an exaggeration
+to claim that misinformation has been deadly for Arizona
+[@pathakInfodemicsCOVID19Role2020].
+
+In academia and policy, the main focus is on the information that is sent to
+consumers, seeing people as passive receivers of information. My dissertation
+instead focuses on individuals as active agents in their search for information
+which helps me uncover the information individuals are exposed to. By looking at
+how individuals search, I aim to identify pain points and focus areas for future
+interventions in the misinformation process.
+
+This research project is important because the vehicles used to search by people
+impacts the information they are exposed to. Given the large swaths of both
+misinformation and disinformation regarding Covid-19 [@mottaHowRightLeaningMedia2020; @pathakInfodemicsCOVID19Role2020; @shahsavariConspiracyTimeCorona2020] and
+the measurable impacts this misinformation has had on pandemic-related health
+behaviors, how we choose to search for information affects our own lives and the
+lives of others. Moreover, individuals who do not utilize social networks for
+information search may feel like they have no network support, leading to
+feelings of network isolation with major implications for mental health 
+[@thoitsMechanismsLinkingSocial2011]
 

### 2022-01-25 paper2.Rmd
Discussion Done

@@
 ---
-title: "Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations "
+title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
 author: "Kelsey Gonzalez"
@@
 output:
+  bookdown::word_document2: 
+    toc: true
+    reference_docx: StylesTemplate.docx
   bookdown::pdf_document2:
@@
     number_sections: true
-  bookdown::word_document2: 
-    toc: true
-    reference_docx: StylesTemplate.docx
 header-includes:
@@
 indent: true
+always_allow_html: true
 ---
@@
 evidence for this thesis. I also investigate which information channels are
-associated with vaccinations against the virus, and find that social netwokring
-sites are associated with lower rates. I also find important ethnocracial
+associated with vaccinations against the virus and find that social networking
+sites are associated with lower rates. I also find important ethnoracial
 differences in information search vehicles utilization and vaccination
@@
 have major ramifications for both the individual and the social world that
-surrounds them. For example, a new found public resistance to vaccination
+surrounds them. For example, a newfound public resistance to vaccination
 against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
@@
 children under the age of five [@givetash19]. However, even in the ever-evolving
-research agenda of misinformation, much of the research focuses on spaces where
-individual first come into contact with conspiracy theories or other information
-rather than what individuals do with the information they obtain
+research agenda of misinformation and infodemiology [@eysenbach02], much of the
+research focuses on the supply side of information, like spaces where
+individuals first encounter with conspiracy theories or other information
 [@johnsonOnlineCompetitionPro2020; @broniatowski_etal20].
@@
 @katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
-“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993].
+“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions 
+@eysenbach09].
 
@@
 
-## subheading - how people search
+## Information Search
 
@@
 information. The most common strategy is browsing, where people follow leads
-based on associations without planning ahead. Another strategy is analytical,
+based on associations without premeditation. Another strategy is analytical,
 which includes an explicit consideration of all facets of the question to guide
@@
 coping with life stresses… that may be exchanged among members of a support
-network” [-@brashersInformationSeekingAvoiding2002, p. 260] <!--  Both of these
+network” [-@brashersInformationSeekingAvoiding2002, p. 260]. <!--  Both of these
 definitions provide important lenses for my question of how computer-mediated or
@@
 “online search”, while the third is conceptually distinct and important to
-include in the survey; yet, it is a hybrid of social network activation and
+include in the survey; yet it is a hybrid of social network activation and
 online search.
@@
 social cost, and the potential avoidance of embarrassment and other negative
-social interactions, I theorize that a majority of people who searched for
+social interactions, I theorize that most people who searched for
 information will have done so online.
@@
 detected usage of a VPN, random answer clicking (determined by illogical
-responses), poor quality typed responses (e.g. social network alters
+responses), poor quality typed responses (e.g., social network alters
 consistently named random nouns), or taking the survey more than once. The same
 is slighted gender unbalanced, slightly skewing towards a male sample. For the
-respondents who provided their zipcode (p = 
+respondents who provided their zip code (p = 
 `r round(nrow(rain[!is.na(rain$region),]) / nrow(rain), 2)`), the 
@@
 for support by segregating weak-tie social support into instrumental, emotional,
-and informational support (see House et al. 1988)). The latter part of the
-survey focuses on resource activation for the specific case-study of information
-during the Covid-19 pandemic and is analyzed in this paper.
+and informational support [see @houseStructuresProcessesSocial1988]. The latter
+part of the survey focuses on resource activation for the specific case-study of
+information during the Covid-19 pandemic analyzed in this paper.
 
@@
     (`Hispanic or Latino/x` = hispanic) +
-    (`Race, Black` = race_white) +
+    (`Race, White` = race_white) +
     (`Race, Black` = race_black) +
@@
 \{`r conf_int_prop(rain$int_sought_fr_dr)`\}).
-About `r print_perc(rain$int_sought_fr_pers)`  said they asked 'a person 
+About `r print_perc(rain$int_sought_fr_pers)` said they asked, 'a person 
 like friend, neighbor, or family member that [they] know' (95% Confidence 
@@
 on a social networking site such as Facebook timeline, Twitter status update, or 
-Linkedin' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
+LinkedIn' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
 Much of the question wording and the specific categories of search were inspired
@@
 
-datasummary(formula = (
-  # (`Income` = income)+  
-                         (`Gender` = gender)+  
+datasummary(formula = ((`Gender` = gender)+  
                          (`Highest Education Level` = educ) + 
@@
 indicating whether the respondent has received a vaccination against Covid-19 or
-plans to. For this survey, the number of doses were unimportant and actually
-having already received the dose were irrelevant to the research question. This
-variable instead focuses on intent or opinion about the vaccine. About 
-`r print_perc(rain$vacc_view_pos)` have a positive view about the vaccine. This
-construct is made through the combination of  two survey items. The first item
-is actual vaccination status, obtained through the question 'Did you receive a
-Covid-19 vaccine?'. `r print_perc(rain$vacc_status)` of the sample said that
-they had indeed received a vaccination (95% Confidence Interval = \{
-`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
+plans to. For this survey, the number of doses or timeline of receipt were less
+relevant to the research question. This variable instead focuses on intent or
+opinion about the vaccine. About `r print_perc(rain$vacc_view_pos)` have a
+positive view about the vaccine. This construct is made through the combination
+of  two survey items. The first item is actual vaccination status, obtained through 
+the question 'Did you receive a Covid-19 vaccine?'.
+`r print_perc(rain$vacc_status)` of the sample said that
+they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
 closer to 55% (CITE), this indicates some bias in our sample that must be
@@
 said they would 'definitely not' receive the vaccine. The variable 'Vaccination
-Outlook' indicates their either the respondent received a Covid-19 vaccine or
+Outlook' indicates that either the respondent received a Covid-19 vaccine or
 either probably or definitely will in the future.
@@
 received information from a social networking site such as Facebook timeline,
-Twitter status update, or linkedin. Finally, the lowest proportion of the sample
+Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
 had received information from an online discussion group, listserve, or other
@@
 female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
-male. The sample is diverse racially though some ethnic groups are under
-represented compared to national averages. Race was evaluated using the
+male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
 question, 'What is your race? If you are "mixed race", select all that apply.'
@@
 Alaskan Native', `r print_perc(rain$race_asian)` selected 'Asian', and finally 
-when asked ' Are you Hispanic, Latino/a/x, or Latin American Origin?', 
+when asked, 'Are you Hispanic, Latino/a/x, or Latin American Origin?', 
 `r print_perc(rain$hispanic)` selected 'Yes'. Respondents were also asked to 
@@
 professional degree',  `r print_perc(rain$college)` of the sample were classified
-to have a College-level education (Associate's degree or above).
+to have a college-level education (Associate's degree or above).
 
@@
 degree of association between two binary variables. ^[To calculate the Phi
-Coefficient, I utilize the Psych `r` package [@psych] ] I then investiage the
+Coefficient, I utilize the Psych `r` package [@psych] ] I then investigate the
 associations between my predictors and the 5 information search vehicles by
@@
 coefficient, with numbers closer to -1 or positive one indicating a very strong
-relationship [@warrens08]. Table \@ref(tab:model-2-chi2) shows the results of
+relationship [@warrens08]. Table \@ref(tab:model-2-phi) shows the results of
 these coefficients. Out of the five information search vehicles investigated,
@@
 coefficients indicate a weak relationship between any two vehicles of
-information search and and that respondents in my sample utilize each of these a
+information search and that respondents in my sample utilize each of these a
 little bit differently.
@@
 
-The first model in Table \@ref(tab:table-model-2) predicts whether or not a
+The first model in Table \@ref(tab:table-model-2) predicts whether a
 respondent sought information intentionally about Covid-19 vaccinations by
@@
 
-The second model predicts whether or not a respondent sought information about
+The second model predicts whether a respondent sought information about
 Covid-19 vaccinations by asking a person like friend, neighbor, or family member
@@
 ( _p_ < 0.01). The unexpected result of this model is that very few factors predict
-personal social network activation and this model has the lowest McFadden's R^2, 
+personal social network activation, and this model has the lowest McFadden's R^2, 
 indicating possible omitted variables.
@@
 less likely to query a forum than those who hadn't (relative odds ratio =
-$1 - exp(\beta k)$, _p_ < 0.01). Morever, I find more ethno-racial effects: 
+$1 - exp(\beta k)$, _p_ < 0.01). Moreover, I find more ethnoracial effects: 
 Respondents who claimed Asian ancestry were 
@@
 Covid-19 vaccinations through posted queries on a social networking site such 
-as Facebook timeline, Twitter status update, or Linkedin. Receiving information
-about Covid-19 seems to be quite related to posting on socia media. Those who 
+as Facebook timeline, Twitter status update, or LinkedIn. Receiving information
+about Covid-19 seems to be quite related to posting on social media. Those who 
 received information from their doctor's had 
@@
 Searching for information using an online search engine such as Google or Bing 
-is theorically the search vehicle with the least amount of social or cognitive 
+is theoretically the search vehicle with the least amount of social or cognitive 
 friction. Our descriptive statistics showed that not everyone used this vehicle,
@@
 higher odds of becoming immunized ( _p_ < 0.001). And finally, I found further
-ethno-racial differences in my sample. I found that Hispanic-Latinos had 
+ethnoracial differences in my sample. I found that Hispanic-Latinos had 
 `r round(exp(mod3$coefficients[['hispanic1']]), 2)` higher odds of vaccination
@@
 they are to seek out information about Covid-19 vaccinations, possibly
-indicating [???? TODO]. Furthermore, I find that those who are more educated,
-that is my respondents who hold an Associate's degree or higher were more likely
-to seek out information; for the most part this trend can be observed in Table
+indicating a larger information need by elderly populations overall, or a more
+pressing need to search for information about the Covid-19 vaccinations because
+of the higher risk of hospitalizations that older populations face
+[@turner_etal18]. Furthermore, I find that those who are more educated, that is
+my respondents who hold an Associate's degree or higher were more likely to seek
+out information; for the most part this trend can be observed in Table
 \@ref(tab:table-model-2) as well. Human Capital Theory [@mirowsky_ross98] may
@@
 as Black were more likely to seek out further information; this may be explained
-by the maltreatment that African-Americans have endured in the US
-healthcare system [@baileyStructuralRacismHealth2017] which has led to major
-distrust of the medical establishment among the population [@center2019a; @murray15].
-
-(May need to cite [@bronson2014don] above or elsewhere)
-
-table 2 main findings
-
-usage of different information search vehicles varies by demographics and also reception of different ifnromation
-- overall, receiving information about Covid-19 vaccination generally spurs information seeking behaviors, though there are variations
-- receive info from doctor leads to searching info from doctor, likely indicates good communication and trust in doctor, solid relationship with healthcare professionals
-- few things predict seeking out information from another person, personal networks are so embedded in everyday life so perhaps don't remember doing it or behavioral prediction is notoriously hard
-- Received Info, Social Networking Site negatively predicts Online Forum, indicating that if your social networks fulfill your need for information you don't need to extend out to online forums to ask for things, need is already met?
-- Asians are really unlikely to use online forums to find information in this context, very strong association but hispanics are more likely than non-hispanics to search online 
-- online search is much less likely from those with higher education, which is counter intuitive since they are the population that has been the most trained in research methods and critical thinking ..
-perhaps they trust the information that they hear if they consider it to be a trusted source (typical higher education format of trust the professor) so they don't look deeper into it?
-basically already have high social capital in other ways, already set up to receive the information they needed and trusted
-- older populations are more likely to 'just google it'
-
-takeaways: Not everyone is activating their personal social networks or using Google in the same rates, the internal variation of users is important to consider when using something like Google Trends
-education really affects information seeking behavior
-ethno-racial differences affect information seeking behavior, more research should look into why there are group differences (likely cultural)
-
-Takeaway 2: in person, online, or search engines?
-
-table 3 main findings 
-- very important for getting people to get vaccinated - a major goal for public Health authorities over the last two years
-- extremely importnat given misinformation around vaccinations 
-- receiving information from a doctor or other medical profession (or seeking) leads to more positive opinions.
-action inspired by this - difficult because of lack of primary care doctors for many americans, but every doctor should discuss the importance for every patient they interact with
-- receiving information from a social networking site NOT an online for results in less vaccinations. 
-- differences in education level and race ; seen in prior literature however most current literature claims that anti-vacination attitudes span social class, political ideology, and X.
-
-social netwokring site
-info from doctor
-
-<!-- this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ...
-<--- I wish I knew what I was talking about here -->
-
-rather than on “the receiver as an active information seeker and processor."
-[@johnsonComprehensiveModelCancerRelated1993].
-
-Est velit egestas dui id ornare arcu odio ut. Tempus iaculis urna id volutpat
-lacus laoreet non curabitur gravida. Integer malesuada nunc vel risus commodo.
-Ipsum nunc aliquet bibendum enim facilisis gravida. Ac turpis egestas maecenas
-pharetra convallis posuere morbi leo. Id diam vel quam elementum pulvinar etiam.
+by the maltreatment that African Americans have endured in the US healthcare
+system [@baileyStructuralRacismHealth2017] which has led to major distrust of
+the medical establishment among the population [@center2019a; @murray15; @bronson2014don].
+
+Table \@ref(tab:table-model-2) further demonstrated important takeaways about
+how individuals seek information. First, I find that the different information
+seeking vehicles queried in this survey are conceptually different and that the
+utilization of different varies by demographic and supply. Overall, receiving
+information about Covid-19 vaccination generally spurs information seeking
+behaviors, though there are key variations. First, if you received information
+from a doctor, you were likely to search from information from a doctor; this
+may indicate an already existing trusting relationship between patient and
+healthcare provider but it may also indicate the healthcare provider, emphasizing
+the importance of the vaccine and the survey respondent seeking out more
+information. Another important finding is that if you received information from
+a Social Networking Site like Facebook or Twitter, you were less likely to query
+Online Forums like Reddit or Facebook Groups; this may be an example of Uses and
+Gratification Theory [@blumlerUsesMassCommunications1974], where the two online
+platforms may act as substitute sources of information and those who were
+satisfied with the information they received on a Social Networking Site didn't
+have the need to seek out more information. Finally, the ethnoracial variations
+exhibited in Table \@ref(tab:table-model-2) likely demonstrate how cultural
+attitudes around the trustworthiness of different sources of information affect
+the utilization of different methods; for example, Asians seem are less likely
+to use online forums than non-Asians while Hispanics are more likely to use them
+than non-Hispanics. The internal variations between the different information
+search vehicles hint at different user profiles and may have major repercussions on
+the quality of information they find and who is exposed to misinformation.
+
+Given the rampant misinformation around Covid-19 and her related vaccinations
+[@pathakInfodemicsCOVID19Role2020] and the slowed rate of vaccinations in the
+United States, it is important to uncover what relationship the different
+fountains of information and information search vehicles for information on this
+topic are associated with compliance with public health recommendations. Table
+\@ref(tab:table-model-3) demonstrated just how these different fountains of
+information and information search vehicles are associated with real world
+consequences through Covid-19 vaccination rates and intentions. The first
+takeaway is that receiving or seeking information from a doctor or other medical
+profession leads to higher likelihood of completed or planned vaccinations.
+While blanket advice like "Healthcare Providers should recommend the vaccine to
+their patients" would be ineffective because of the declining number of
+Americans with a primary care doctor [@levine_etal20], increasing trust in the
+institution of medicine seems to remain a strong predictor of vaccinations. 
+<!-- add more here, there is a huge logical and sampling fallacy here --> 
+A second major takeaway is that receiving information from a Social Networking
+Site like Facebook timeline or Twitter status update was significantly
+associated with lower vaccination rates. While we don't know what exact
+information was absorbed on these platforms, the lower odds of vaccination
+indicate that it was not positive. Much has been attempted between 2020 and 2022
+to curb vaccine misinformation on these social networking platforms [see
+@bowman20 for an early example]; however, I find evidence that these social
+networking platforms nevertheless have a measurable negative impact. Finally,
+this studies also contributes to the conversation on ethnoracial and
+educational differences in vaccine hesitancy. I find in my sample that
+Hispanic-Latinos were more likely than non-Hispanics and Asians more likely
+than non-Asians to receive or plan to receive a vaccination against Covid-19
+(Table \@ref(tab:table-model-3)). However, these findings sometimes misalign
+with other studies that show that Whites have the lowest levels of vaccine
+hesitancy and many minorities are much more hesitant [@momplaisir_etal21;
+@foxworth21], though some research indeed finds higher levels of institutional
+trust from the Asian subsample [@bagasra_etal21] or are consistent with my
+findings [@king_etal21]. My finding that higher educated people, that is: my
+population that holds an associated degree or above, are more likely seek
+vaccination is largely consistent with the broader literature
+[@khairat_etal22], though there are many variations depending on the vaccine
+in question [@siddiqui_etal13].
+
+```{r include = FALSE}
+plot_df <- tribble(~vacc_view_pos, ~n, ~race)
+
+plot_df <- rain %>% 
+  count(race_asian, vacc_view_pos) %>% 
+  filter(race_asian == T) %>% 
+  mutate(race = 'Asian') %>% 
+  select(-race_asian) %>% 
+  bind_rows(plot_df)
+
+plot_df <- rain %>% 
+  count(race_white, vacc_view_pos) %>% 
+  filter(race_white == T) %>% 
+  mutate(race = 'White') %>% 
+  select(-race_white) %>% 
+  bind_rows(plot_df)
+
+plot_df <- rain %>% 
+  count(race_black, vacc_view_pos) %>% 
+  filter(race_black == T) %>% 
+  mutate(race = 'Black') %>% 
+  select(-race_black) %>% 
+  bind_rows(plot_df)
+
+plot_df <- rain %>% 
+  count(race_nat, vacc_view_pos) %>% 
+  filter(race_nat == T) %>% 
+  mutate(race = 'Native American') %>% 
+  select(-race_nat) %>% 
+  bind_rows(plot_df)
+
+plot_df <- rain %>% 
+  count(hispanic, vacc_view_pos) %>% 
+  filter(hispanic == T) %>% 
+  mutate(race = 'Hispanic') %>% 
+  select(-hispanic) %>% 
+  bind_rows(plot_df)
+
+race_plot <- plot_df %>% 
+  filter(!is.na(vacc_view_pos)) %>% 
+  group_by(race) %>% 
+  mutate(total = sum(n),
+         perc = n/total,
+         vacc_view_pos = fct_recode(factor(vacc_view_pos), Negative = '0', Positive = '1')) %>% 
+  ggplot(aes(x = fct_reorder2(race, vacc_view_pos, perc), y = perc, fill = vacc_view_pos)) + 
+  geom_col(position = 'dodge') +
+  scale_y_continuous(labels = percent_format(), expand = c(0,0)) + 
+  ylab("") + xlab("") + 
+  theme_diss()+
+  labs(fill = "Vaccinated\n or plans to") +
+  scale_fill_manual(values = my_palette[c(2, 8)]) +
+  coord_flip()
+educ_plot <- rain %>% 
+  count(educ, vacc_view_pos) %>% 
+  filter(!is.na(vacc_view_pos),
+         educ != 'Less than high school') %>% 
+  group_by(educ) %>% 
+  mutate(total = sum(n),
+         perc = n/total,
+         vacc_view_pos = fct_recode(factor(vacc_view_pos), Negative = '0', Positive = '1')) %>% 
+  ggplot(aes(x = educ, y = perc, fill = vacc_view_pos)) + 
+  geom_col(position = 'dodge') +
+  scale_y_continuous(labels = percent_format(), expand = c(0,0)) + 
+  ylab("") + xlab("") +
+  theme_diss()+
+  labs(fill = "Vaccinated\n or plans to") +
+  scale_fill_manual(values = my_palette[c(2, 8)])  +
+  coord_flip()
+
+library(patchwork)
+(race_plot + educ_plot)+ plot_layout(guides = "collect") + patchwork::plot_annotation(title = "Percent Vaccinated Against Covid-19", caption = glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021."))
+
+```
 
@@
 
-In academia and policy, the main focus is on the information that is sent to
+In academia and policy, the focus is on the information that is sent to
 consumers, seeing people as passive receivers of information. My dissertation
@@
 
+\newpage
+
 # References {-}
@@
 \newpage
+
 # Appendix 1: Survey Questions
@@
 *	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
-*	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
+*	From a social networking site such as Facebook timeline, Twitter status update, or LinkedIn?  (12) 
 *	Other  (13) _______
@@
 *	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
-*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  (6) 
+*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn  (6) 
 *	Searched for my question using an online search engine such as Google or Bing  (7) 

### 2022-01-26 paper2.Rmd
conclusion written

@@
 output:
+  bookdown::pdf_document2:
+    latex_engine: xelatex
+    number_sections: true
   bookdown::word_document2: 
@@
     reference_docx: StylesTemplate.docx
-  bookdown::pdf_document2:
-    latex_engine: xelatex
-    number_sections: true
 header-includes:
@@
                       warning = FALSE,
-                      cache = TRUE,
+                      # cache = TRUE,
                       fig.width = 7,
@@
   max <- p + 1.96*sqrt((p*q)/n) 
-  paste0(round(min, 2), ", ", round(max, 2))
+  paste0(label_percent()(min), ", ", label_percent()(max))
 }
@@
 
+Keywords: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks,
+
 # Intro
@@
 research agenda of misinformation and infodemiology [@eysenbach02], much of the
-research focuses on the supply side of information, like spaces where
+research focuses on the 'push' or 'supply' side of information, like spaces where
 individuals first encounter with conspiracy theories or other information
@@
 
-The lack of research in this area makes it quite unclear how individuals choose
-to search for information through the multimedia environment of the 21st
-century. Even outside of the misinformation literature, much of the research
-conducted in social networks and communication focus on senders, influencers,
-and persuasion strategies [@mertonManifestLatentFunctions1968;
+The lack of research in which vehicles are likely to be chosen when an
+individual faces a need for information makes it difficult for policy makers to
+propose effective information campaigns that promote the health and wellbeing of
+individuals in our society. Even outside of the misinformation literature, much
+of the research conducted in social networks and communication focus on senders,
+influencers, and persuasion strategies [@mertonManifestLatentFunctions1968;
 @katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
-“the receiver as an active information seeker and processor."   [@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions 
+“the receiver as an active information seeker and processor."
+[@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions
 @eysenbach09].
 
-<!-- TODO cleanup -->
-For this paper, I will use the case of Covid-19 vaccinations to explore the
-variation among information search vehicles. T
-
-Research Questions
-
-* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
-* What factors lead people to perform health information search online versus among social network ties? 
-* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?
-
-<!-- TODO  cleanup -->
+I use the case of information around Covid-19 vaccinations to explore the
+variation of usage of information search vehicles. In doing so, I seek to answer
+how computer-mediated or interpersonal information-seeking strategies vary
+across populations in their search for information about Covid-19 vaccinations
+and investigate how these strategies affect vaccination uptake.
+
+Before addressing my central research questions, I offer an overview of the
+current state of social science literature in regards to infromation-seeking
+strategies before providing a description of the research methodology and
+analytic sample. I discuss the implications of these findings for the
+sociological understanding of information search and vaccination uptake.
 
@@
 
-Active directed searching by individuals to obtain information is sparsely
+Active, directed searching by individuals to obtain information is sparsely
 discussed in the sociological literature. Pejtersen
@@
 information-search; rather, it is driven by a discrepancy between the current
-level of uncertainty on a subject and desired level of uncertainty.
+level of uncertainty on a subject and desired level of uncertainty. In other
+words, individuals only perform information search when they are distressed by
+their lack of knowledge or understanding on a subject.
 
@@
 coping with life stresses… that may be exchanged among members of a support
-network” [-@brashersInformationSeekingAvoiding2002, p. 260]. <!--  Both of these
-definitions provide important lenses for my question of how computer-mediated or
-interpersonal information-seeking strategies vary.--> If information is needed
-but there is no search for coping or deeper understanding of important matters,
-people are likely to choose to search online.
-
-Core discussion networks are the default lens to investigate network resources
-and social support in surveys. The underlying assumption is that individuals
-reach out to a handful of strong ties when in need of support, which can be
-elicited in surveys using name generators [@marsdenCoreDiscussionNetworks1987].
-This approach has yielded important insights, but largely overlooks crucial
+network” [-@brashersInformationSeekingAvoiding2002, p. 260]. These definitions
+help to differentiate between seeking information through social ties or through
+something anonymous like online search; a need for coping or deeper
+understanding of important matters is thought to sway that decision.
+
+Social support has long been theorized to stem from core discussion networks and
+much of the historical social support surveys only looked at these core
+networks. The underlying assumption is that individuals reach out to a handful
+of strong ties when in need of support, which could be elicited in surveys using
+name generators [@marsdenCoreDiscussionNetworks1987]. This approach has yielded
+important insights, but largely overlooks crucial
 processes of resource activation [@hurlbertCoreNetworksTie2000;
-@perrySocialNetworkActivation2015; @smithDonPutMy2005]. Small
+@perrySocialNetworkActivation2015; @smithDonPutMy2005]. For instance, Small
 [-@smallSomeoneTalk2017] shows that the core discussion network does not capture
 how people activate social support in practice and indicates that people draw on
-much broader social connections for support, also calling back to the weak ties
+much broader social connections for support, reminiscent of the weak ties
 research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
@@
 [-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
-informational support. I follow the definition of Cohen and Wills
-[-@cohenStressSocialSupport1985] and define informational support as “help in
-defining, understanding,  and coping with problematic events and include
-education, advice, or referral to another source of  support”
-[@winemiller_etal93, p. 640].
+informational support.
 
@@
 simply "happened to be there", online search is theoretically the most
-frictionless and costless mode of support. There are three computer-mediated
-vehicles I consider for this analysis: search engines like Google, posting
-questions on online forums like subreddits or Facebook groups, and posting a
-status update online via Facebook or Twitter. The first two comprise what I call
-“online search”, while the third is conceptually distinct and important to
-include in the survey; yet it is a hybrid of social network activation and
-online search.
-
-From studies of mass communication, uses and gratifications theory (UGT)
-[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985] may also
-lend itself to theorizing why computer-mediated or interpersonal
-information-seeking strategies vary. UGT posits that users are not passive
-consumers of media and that people have an active role in choosing different
-sources of media based on their satisfaction of specific needs on an individual
-basis. UGT is based on Maslow’s [-@maslowTheoryHumanMotivation1943] hierarchy of
-needs and is compatible with Lazarsfeld and Katz’s theory of two-step flow
-[-@katzPersonalInfluencePart1955] because people can choose their media and the
-opinion leaders they follow. Modern-day theorists have extended UGT theory and
-classified the uses and gratifications of the internet and of social media.
-Stafford, Stafford, and Schkade [-@staffordDeterminingUsesGratifications2004]
-theorize that the internet provides gratification through useful content that
-meets expectations, gratification from purposeful navigating or random browsing
-as a process, and social gratification from forming and deepening social ties.
-Leung [-@leungGenerationalDifferencesContent2013] theorizes that social media is
+frictionless and costless mode of support. No social capital or relationship is
+necessary when chosing to utilize a search engine.
+
+There are three computer-mediated vehicles I consider for this analysis: online
+search engines like Google or Bing, posting questions on online forums like
+subreddits or Facebook groups, and posting a status update online via Facebook
+or Twitter. While the first two are largely anonymous and don't require a
+personal network, the third is a unique hybrid between personal network
+connections and online search.
+
+There are important factors that can influence information-seeking strategies
+besides the strength of social capital or ease of search. For instance, we can
+borrow uses and gratifications theory (UGT) from studies of mass communication
+[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985]. UGT
+posits that users are not passive consumers of media and that people have an
+active role in choosing different sources of media based on their satisfaction
+of specific needs on an individual basis. UGT is based on Maslow’s
+[-@maslowTheoryHumanMotivation1943] hierarchy of needs and is compatible with
+Lazarsfeld and Katz’s theory of two-step flow [-@katzPersonalInfluencePart1955]
+because people can choose their media and the opinion leaders they follow.
+Modern-day theorists have extended UGT theory and classified the uses and
+gratifications of the internet and of social media. Stafford, Stafford, and
+Schkade [-@staffordDeterminingUsesGratifications2004] theorize that the internet
+provides gratification through useful content that meets expectations,
+gratification from purposeful navigating or random browsing as a process, and
+social gratification from forming and deepening social ties. Leung
+[-@leungGenerationalDifferencesContent2013] theorizes that social media is
 gratifying for users because it allows for venting of negative feelings,
 provides recognition, provides entertainment, promotes social affection, and
-fulfills cognitive needs. Adapting UGT to my own purposes, I theorize that
-informational support will be activated from network ties when the informational
-need is related to forming and deepening social ties but search will be
-conducted online when information is needed but an individual does not have an
-additional cognitive need to fill through social interaction. Alternative goals
-such as identity management or relational maintenance
-[@brashersInformationSeekingAvoiding2002] need to be balanced and will determine
-where search is conducted.
-
-<!-- connect above and below paragraph to flow together -->
-<!-- TODO  cleanup -->
-
-As online search or interaction also allows increased anonymity, no or lowered
-social cost, and the potential avoidance of embarrassment and other negative
-social interactions, I theorize that most people who searched for
-information will have done so online.
-
-there are theoretical reasons why individuals would choose to search for
-information among their network ties instead of online search. For instance,
-Rains [-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
-technical information about an illness online but turn to their social network
-for experiential information from others facing similar circumstances in the
-case of cancer. Moreover, if an individual distrusts the medical establishment,
-or popular media, they may be more likely to activate informational support
-among their social network or turn to online groups that validate their
-worldview [@bogersHowSocialAre2014].
-
-<!-- TODO add a hypothesis here -->
+fulfills cognitive needs.
+
+Adapting these facets of UGT and social support to my own case, I theorize that
+online search allows for increased anonymity, a lowered social cost, and the
+potential avoidance of embarrassment and other negative social interactions,
+especially in the case on search engines. Stephen Rains
+[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
+technical information about an illness online but they then turn to their social
+network for experiential information from others facing similar circumstances in
+the case of cancer. The type of information sought is therefore important.
+If specific expertise on a specific topic is desired by a searcher, they may
+reach out to personal connections that they see as expert such as a doctor, or
+if an individual distrusts the medical establishment, they may be more likely to
+activate informational support among their social network or turn to online
+groups that validate their worldview [@bogersHowSocialAre2014]. Finally, UGT and
+Brasher's definition of social support
+[-@brashersInformationSeekingAvoiding2002] help us to theorize that the
+psychosocial needs like identity management or relational maintenance
+[@brashersInformationSeekingAvoiding2002] of an individual may influence their
+chosen information search vehicle: when the informational need is related to
+forming and deepening social ties search is likely to be done from network ties.
 
@@
     (`Vaccination Status` = vacc_status) +
-    (`Vaccination Favorability` = vacc_view_pos) +
+    (`Vaccination Outlook` = vacc_view_pos) +
     (`Age` = age) +
@@
 Another Dependent variable for this analysis is a dichotomous variable
-indicating whether the respondent has received a vaccination against Covid-19 or
-plans to. For this survey, the number of doses or timeline of receipt were less
+indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
 relevant to the research question. This variable instead focuses on intent or
@@
 they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
-closer to 55% (CITE), this indicates some bias in our sample that must be
+closer to 75% [@cdc20], this indicates some bias in our sample that must be
 acknowledged: either MTurkers are more likely to be vaccinated that the normal
@@
 from)'. This differs from the 'How did you look for information' question above
-because it is based on passive reception of information. The largest proportion
+because this is based on passive reception of information. The largest proportion
 of respondents had received information from a person like friend, neighbor, or
@@
 ```{r clean_before_reg}
-rain <- rain %>% 
+rain_mod <- rain %>% 
   mutate(across(c(receive_i,
@@
               college,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 nullmod1 <- glm(formula = int_sought ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 psuedor2 <- as.numeric(1-(logLik(mod1)/logLik(nullmod1)))
@@
 the Covid-19 vaccine?" Because respondents could select as many responses as
-applicable, each response is recorded as a dichotomous variable. I first
-investigate how each Information Search Vehicle are related to each other using
-the Phi Coefficient ($\\phi$) of binary association between each Information
-Search Vehicle pair. The Phi coefficient can be interpreted like a correlation
-coefficient, with numbers closer to -1 or positive one indicating a very strong
-relationship [@warrens08]. Table \@ref(tab:model-2-phi) shows the results of
-these coefficients. Out of the five information search vehicles investigated,
-there is evidence that the vehicles are distinctly different concepts because
-most coefficients fall under 0.3, the general rule of thumb for correlation 
+applicable, each response is recorded as a dichotomous variable. Table 
+\@ref(tab:table-1-desc) reveals differences in the prevalence of usage of the 
+various information seeking vehicles: Around 40% of the sample has inquired for 
+information from a doctor, a person, or using online search tool (
+`r percent_format()(mean(rain$int_sought_fr_dr, na.rm = T))`, 
+`r percent_format()(mean(rain$int_sought_fr_pers, na.rm = T))`,
+`r percent_format()(mean(rain$int_sought_fr_onlsearch, na.rm = T))`) while my 
+respondents used vehicles like online forums (
+`r percent_format()(mean(rain$int_sought_fr_onlgroup, na.rm = T))`) and social
+networking sites (`r percent_format()(mean(rain$int_sought_fr_onlnet, na.rm = T))`)
+to seek out information at significantly lower rates. To investigate how each
+Information Search Vehicle are related to each other using the Phi Coefficient
+($\\phi$) of binary association between each Information Search Vehicle pair.
+The Phi coefficient can be interpreted like a correlation coefficient, with
+numbers closer to -1 or positive one indicating a very strong relationship
+[@warrens08]. Table \@ref(tab:model-2-phi) shows the results of these
+coefficients. Out of the five information search vehicles investigated, there is
+evidence that the vehicles are distinctly different concepts because most
+coefficients fall under 0.3, the general rule of thumb for correlation
 coefficients to indicate a relationship. There does seem to be a relationship
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
+         data = rain_mod, family = binomial(link="logit"))
 
@@
            race_white + race_black + race_nat + race_asian + hispanic,  
-         data = rain, family = binomial(link="logit"))
+         data = rain_mod, family = binomial(link="logit"))
 
 moda <- glm(formula = int_sought_fr_dr ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 r2_a <- as.numeric(1-(logLik(part2_models[['Doctor']])/logLik(moda)))
@@
 modb <- glm(formula = int_sought_fr_pers ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 r2_b <- as.numeric(1-(logLik(part2_models[['Person']])/logLik(modb)))
@@
 modc <- glm(formula = int_sought_fr_onlgroup ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 r2_c <- as.numeric(1-(logLik(part2_models[['Online Forum']])/logLik(modc)))
@@
 modd <- glm(formula = int_sought_fr_onlnet ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 r2_d <- as.numeric(1-(logLik(part2_models[['Social Networking Site']])/logLik(modd)))
@@
 mode <- glm(formula = int_sought_fr_onlsearch ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 r2_e <- as.numeric(1-(logLik(part2_models[['Online Search']])/logLik(mode)))
@@
            college,  
-         data = rain, family = binomial(link="logit"))
+         data = rain_mod, family = binomial(link="logit"))
 
 nullmod3 <- glm(formula = vacc_view_pos ~ 1,
-            data = rain, family = binomial(link="logit"))
+            data = rain_mod, family = binomial(link="logit"))
 psuedor2_mod3 <- as.numeric(1-(logLik(mod3)/logLik(nullmod3)))
@@
 of the higher risk of hospitalizations that older populations face
-[@turner_etal18]. Furthermore, I find that those who are more educated, that is
-my respondents who hold an Associate's degree or higher were more likely to seek
-out information; for the most part this trend can be observed in Table
-\@ref(tab:table-model-2) as well. Human Capital Theory [@mirowsky_ross98] may
-help to explain this finding; this theory claims that education helps
-individuals gaining health-related knowledge and use this knowledge to be
-proactive in their own lives. Finally, I find that my respondents who identified
-as Black were more likely to seek out further information; this may be explained
-by the maltreatment that African Americans have endured in the US healthcare
-system [@baileyStructuralRacismHealth2017] which has led to major distrust of
-the medical establishment among the population [@center2019a; @murray15; @bronson2014don].
+[@turner_etal18]. Furthermore, I find that those who are college educated were
+more likely to seek out information; for the most part this trend can be
+observed in Table \@ref(tab:table-model-2) as well. Human Capital Theory
+[@mirowsky_ross98] may help to explain this finding; this theory claims that
+higher education can provides the skills to gain health-related knowledge and
+use this knowledge to be proactive in their own lives. Finally, I find that my
+respondents who identified as Black were more likely to seek out further
+information; this may be explained by the maltreatment that African Americans
+have endured in the US healthcare system [@baileyStructuralRacismHealth2017]
+which has led to major distrust of the medical establishment among the
+population [@center2019a; @murray15; @bronson2014don].
 
@@
 seeking vehicles queried in this survey are conceptually different and that the
-utilization of different varies by demographic and supply. Overall, receiving
-information about Covid-19 vaccination generally spurs information seeking
-behaviors, though there are key variations. First, if you received information
-from a doctor, you were likely to search from information from a doctor; this
-may indicate an already existing trusting relationship between patient and
-healthcare provider but it may also indicate the healthcare provider, emphasizing
-the importance of the vaccine and the survey respondent seeking out more
-information. Another important finding is that if you received information from
-a Social Networking Site like Facebook or Twitter, you were less likely to query
-Online Forums like Reddit or Facebook Groups; this may be an example of Uses and
-Gratification Theory [@blumlerUsesMassCommunications1974], where the two online
-platforms may act as substitute sources of information and those who were
-satisfied with the information they received on a Social Networking Site didn't
-have the need to seek out more information. Finally, the ethnoracial variations
-exhibited in Table \@ref(tab:table-model-2) likely demonstrate how cultural
-attitudes around the trustworthiness of different sources of information affect
-the utilization of different methods; for example, Asians seem are less likely
-to use online forums than non-Asians while Hispanics are more likely to use them
-than non-Hispanics. The internal variations between the different information
-search vehicles hint at different user profiles and may have major repercussions on
-the quality of information they find and who is exposed to misinformation.
-
-Given the rampant misinformation around Covid-19 and her related vaccinations
-[@pathakInfodemicsCOVID19Role2020] and the slowed rate of vaccinations in the
+utilization of different varies by demographic and supply (information fountain?
+~ source of having receiving information). Overall, receiving information about
+Covid-19 vaccination generally is associated with information seeking behaviors,
+though there are key variations. First, if you received information from a
+doctor, you were likely to search from information from a doctor; this may
+indicate an already existing trusting relationship between patient and
+healthcare provider but it may also indicate the healthcare provider taking
+initiaive and emphasizing the importance of the vaccine or the survey respondent
+seeking out information from an expert. Another important finding is that if you
+received information from a Social Networking Site like Facebook or Twitter, you
+were less likely to query Online Forums like Reddit or Facebook Groups; this may
+be an example of Uses and Gratification Theory
+[@blumlerUsesMassCommunications1974], where the two online platforms may act as
+substitute sources of information and those who were satisfied with the
+information they received on a Social Networking Site didn't have the need to
+seek out more information. Finally, the ethnoracial variations exhibited in
+Table \@ref(tab:table-model-2) likely demonstrate how cultural attitudes around
+the trustworthiness of different sources of information affect the utilization
+of different methods; for example, Asians seem are less likely to use online
+forums than non-Asians while Hispanics are more likely to use them than
+non-Hispanics. The internal variations between the different information search
+vehicles hint at different user profiles and may have major repercussions on the
+quality of information they find and who is exposed to poor quality information.
+
+Given the rampant misinformation around Covid-19, her related vaccinations
+[@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020; 
+@shahsavariConspiracyTimeCorona2020] and the slowed rate of vaccinations in the
 United States, it is important to uncover what relationship the different
-fountains of information and information search vehicles for information on this
-topic are associated with compliance with public health recommendations. Table
+fountains of information and information search vehicles for Covid-19 vaccinations
+are associated with compliance with public health recommendations. Table
 \@ref(tab:table-model-3) demonstrated just how these different fountains of
@@
 networking platforms nevertheless have a measurable negative impact. Finally,
-this studies also contributes to the conversation on ethnoracial and
+this study also contributes to the conversation on ethnoracial and
 educational differences in vaccine hesitancy. I find in my sample that
-Hispanic-Latinos were more likely than non-Hispanics and Asians more likely
-than non-Asians to receive or plan to receive a vaccination against Covid-19
-(Table \@ref(tab:table-model-3)). However, these findings sometimes misalign
-with other studies that show that Whites have the lowest levels of vaccine
-hesitancy and many minorities are much more hesitant [@momplaisir_etal21;
-@foxworth21], though some research indeed finds higher levels of institutional
-trust from the Asian subsample [@bagasra_etal21] or are consistent with my
-findings [@king_etal21]. My finding that higher educated people, that is: my
-population that holds an associated degree or above, are more likely seek
+Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
+to receive or plan to receive a vaccination against Covid-19 (Table
+\@ref(tab:table-model-3)). Research in this area has mixed results, with some
+studies showcasing consistent findings to these [@bagasra_etal21; @king_etal21],
+while others show that Whites have the lowest levels of vaccine hesitancy and
+many minorities are much more hesitant [@momplaisir_etal21;
+@foxworth21]. My finding that college-educated respondents were more likely seek
 vaccination is largely consistent with the broader literature
-[@khairat_etal22], though there are many variations depending on the vaccine
-in question [@siddiqui_etal13].
+[@khairat_etal22], though again there are many variations depending on the vaccine
+in question and study context [@siddiqui_etal13].
 
@@
 Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. In this paper, I aim to
-uncover just how different various methods of information search are and begin a
-line of research inquiry that investigates the factors associated with each vehicle. 
-Finally, I also aimed to uncover how the different fountains of information and
-information search vehicles hold real world consequences through their associations
-with Covid-19 vaccination rates and intentions.
-
-The vaccines against the COVID-19 coronavirus prevent severe illness,
-hospitalization, and death. However, as I’m writing this, less than 55% of
-Arizonans over 12 years old are fully vaccinated against the virus. We know that
-people exposed to misinformation are much less likely to receive vaccinations
-against the virus [@loombaMeasuringImpactCOVID192021]. It is not an exaggeration
-to claim that misinformation has been deadly for Arizona
-[@pathakInfodemicsCOVID19Role2020].
-
-In academia and policy, the focus is on the information that is sent to
-consumers, seeing people as passive receivers of information. My dissertation
-instead focuses on individuals as active agents in their search for information
-which helps me uncover the information individuals are exposed to. By looking at
-how individuals search, I aim to identify pain points and focus areas for future
-interventions in the misinformation process.
-
-This research project is important because the vehicles used to search by people
-impacts the information they are exposed to. Given the large swaths of both
-misinformation and disinformation regarding Covid-19 [@mottaHowRightLeaningMedia2020; @pathakInfodemicsCOVID19Role2020; @shahsavariConspiracyTimeCorona2020] and
-the measurable impacts this misinformation has had on pandemic-related health
-behaviors, how we choose to search for information affects our own lives and the
-lives of others. Moreover, individuals who do not utilize social networks for
-information search may feel like they have no network support, leading to
-feelings of network isolation with major implications for mental health 
-[@thoitsMechanismsLinkingSocial2011]
+information seeking behaviors online and offline and largely focuses on the
+information that is sent to consumers [push], seeing people as passive receivers
+of information. In this paper, I instead focus on individuals as active agents
+in their search for information to  begin a line of research inquiry that
+investigates the factors associated with the various methods of information
+search.
+
+Given the large swaths of both misinformation and disinformation regarding
+Covid-19 [@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020;
+@shahsavariConspiracyTimeCorona2020] and the measurable impacts this
+misinformation has had on pandemic-related health behaviors
+[@loombaMeasuringImpactCOVID192021], Covid-19 provides an ideal study to
+investigate how we choose to search for information that affects both our own
+lives and the lives of others.
+
+This paper has provided several key findings that can be used to motivate policy
+interventions for the Covid-19 vaccination campaigns and in the future for other
+information campaigns. However, these findings are not to be taken out of the
+context of their limitations. This paper is built off a small survey sample (`r
+nrow(rain)`) that was hosted online and anonymously through MTurk, a service
+that provides people with micro-jobs. Because of how the website is set up,
+respondents are incentivized to fill out surveys as quick as possible and there
+were many responses that were poor quality and removed from the sample before
+analysis. Moreover, there is no incentive for respondents to be honest in these
+surveys. However, each of these limitations are often pointed to as limitations 
+of survey research as a whole.
+
+Overall, this research project is important because the vehicles used in
+information search impacts the information and quality of information found By
+looking at how individuals search, I aim to identify pain points and focus areas
+for future interventions in the misinformation process.
 

### 2022-01-26 paper2.Rmd
FIRST DRAFT COMPLETE !!!!

@@
 # Abstract 
-How do individuals perform information search, and what factors help them decide
-which information search vehicle to utilize, such as interpersonal networks or
-online tools, I investigate the above question using individual survey data of
-934 Adults in the United States and find that X and Y. Furthermore, this paper
-demonstrates that searching for a question online using a search engine or
-social network was more common than traditional means of information gathering,
-such as network activation (asking someone in their social network for
-informational support). Using X and Y theory I predict that that few people will
-activate their social network for informational support in my chosen case of
-Covid-19 vaccinations because of the social cost of doing so but fail to find
-evidence for this thesis. I also investigate which information channels are
-associated with vaccinations against the virus and find that social networking
-sites are associated with lower rates. I also find important ethnoracial
-differences in information search vehicles utilization and vaccination
-reception.
-
-<!-- TODO this needs a lot of work but its a start -->
 Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. In this paper, I aim to
-uncover just how different various methods of information search are and begin a
-line of research inquiry that investigates the factors associated with each vehicle. 
-Finally, I also aimed to uncover how the different fountains of information and
-information search vehicles hold real world consequences through their associations
-with Covid-19 vaccination rates and intentions.
-
-Keywords: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks,
+information seeking behaviors online and offline. Using theories of social
+support and uses and gratifications theory I investigate the factors associated
+with each vehicle type when on information seeking vehicle: personal connection,
+doctor, social networking site, online forum, and online search engine. Using
+novel survey data of `r nrow(rain)` Americans and their experience seeking out
+information about the Covid-19 vaccines, I find little evidence that online
+search is more utilized than seeking social support from personal network
+connections or health professionals. I find evidence that the vehicles queried
+in this survey are conceptually different and that the utilization of different
+vehicles varies by demography and information sources. Finally, I find that
+different fountains of information and information search vehicles hold real
+world consequences through their associations with Covid-19 vaccination rates
+and intentions, as information from a doctor increased the Covid-19 vaccination
+uptake while receiving information from a Social Networking Site like Facebook
+or Twitter was associated with lower odds of vaccination.
+
+**Keywords**: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information & Communication Technologies
 

### 2022-02-02 paper2.Rmd
spelling

@@
 takeaway is that receiving or seeking information from a doctor or other medical
-profession leads to higher likelihood of completed or planned vaccinations.
+profession was associated with higher likelihood of completed or planned vaccinations.
 While blanket advice like "Healthcare Providers should recommend the vaccine to
@@
 information campaigns. However, these findings are not to be taken out of the
-context of their limitations. This paper is built off a small survey sample (`r
-nrow(rain)`) that was hosted online and anonymously through MTurk, a service
+context of their limitations. This paper is built off a small survey sample (
+`r nrow(rain)`) that was hosted online and anonymously through MTurk, a service
 that provides people with micro-jobs. Because of how the website is set up,
@@
 were many responses that were poor quality and removed from the sample before
-analysis. Moreover, there is no incentive for respondents to be honest in these
-surveys. However, each of these limitations are often pointed to as limitations 
-of survey research as a whole.
+analysis. Because of this, there is no incentive for respondents to be honest in
+these surveys. However, each of these limitations are often pointed to as
+limitations of survey research as a whole. Even given these limitations,
+the finding of this paper are interesting contributions to the literature.
 
 Overall, this research project is important because the vehicles used in
-information search impacts the information and quality of information found By
-looking at how individuals search, I aim to identify pain points and focus areas
-for future interventions in the misinformation process.
+information search impacts the information and quality of information found. By
+looking at how individuals search, I aim to identified pain points and focus areas
+for future interventions (receiving information online; ethnoracial variations; ) in the misinformation process.
 

### 2022-06-18 paper2.Rmd
Final version of dissertation paper 2

--- 2022-01-26 paper2.Rmd
@@
 
-# Abstract 
-Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. Using theories of social
-support and uses and gratifications theory I investigate the factors associated
-with each vehicle type when on information seeking vehicle: personal connection,
-doctor, social networking site, online forum, and online search engine. Using
-novel survey data of `r nrow(rain)` Americans and their experience seeking out
-information about the Covid-19 vaccines, I find little evidence that online
-search is more utilized than seeking social support from personal network
-connections or health professionals. I find evidence that the vehicles queried
-in this survey are conceptually different and that the utilization of different
-vehicles varies by demography and information sources. Finally, I find that
-different fountains of information and information search vehicles hold real
-world consequences through their associations with Covid-19 vaccination rates
-and intentions, as information from a doctor increased the Covid-19 vaccination
-uptake while receiving information from a Social Networking Site like Facebook
-or Twitter was associated with lower odds of vaccination.
-
-**Keywords**: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information & Communication Technologies
-
-# Intro
-
-Information is all around us and permeates every facet of human society, from
-the hordes of data gathered during the internet age or passing gossip between
-friends. Human communication and human society are based on the circulation of
-information and knowledge. Information can be shared by others through
-information campaigns and consumed by an individual, called information push, or
-intentionally sought out by individuals, called information pull 
-[@cybenkoFoundationsInformationPush1999].
-
-Information is especially important given the prominent trends of
-misinformation, disinformation, and mistrust in traditional institutions
-[@starbird19; @kata10]. While no belief in false information can be thought of as
-harmless [@douglas21] some discredited theories such as 'vaccines cause autism'
-have major ramifications for both the individual and the social world that
-surrounds them. For example, a newfound public resistance to vaccination
-against Measles by so-called 'anti-vaxxers' caused a 17% increase in rates
-worldwide in 2019. This increase killed  142,000 people, most of whom were
-children under the age of five [@givetash19]. However, even in the ever-evolving
-research agenda of misinformation and infodemiology [@eysenbach02], much of the
-research focuses on the 'push' or 'supply' side of information, like spaces where
-individuals first encounter with conspiracy theories or other information
-[@johnsonOnlineCompetitionPro2020; @broniatowski_etal20].
-<!-- cite something else here -->
-
-The lack of research in which vehicles are likely to be chosen when an
-individual faces a need for information makes it difficult for policy makers to
-propose effective information campaigns that promote the health and wellbeing of
-individuals in our society. Even outside of the misinformation literature, much
-of the research conducted in social networks and communication focus on senders,
-influencers, and persuasion strategies [@mertonManifestLatentFunctions1968;
-@katzPersonalInfluencePart1955; @lazarsfeldPeopleChoice1944 ], rather than on
-“the receiver as an active information seeker and processor."
-[@johnsonComprehensiveModelCancerRelated1993; though there are always exceptions
-@eysenbach09].
-
-I use the case of information around Covid-19 vaccinations to explore the
-variation of usage of information search vehicles. In doing so, I seek to answer
-how computer-mediated or interpersonal information-seeking strategies vary
-across populations in their search for information about Covid-19 vaccinations
-and investigate how these strategies affect vaccination uptake.
-
-Before addressing my central research questions, I offer an overview of the
-current state of social science literature in regards to infromation-seeking
-strategies before providing a description of the research methodology and
-analytic sample. I discuss the implications of these findings for the
-sociological understanding of information search and vaccination uptake.
-
-## Information Search
-
-Active, directed searching by individuals to obtain information is sparsely
-discussed in the sociological literature. Pejtersen
-[-@pejtersenDesignComputeraidedUsersystem1984], a scholar of library and
-information science, theorized that there are 5 strategies for searching for
-information. The most common strategy is browsing, where people follow leads
-based on associations without premeditation. Another strategy is analytical,
-which includes an explicit consideration of all facets of the question to guide
-a search. The empirical method guides the search based on tactics that were
-successful in past research. The known site strategy is to go to the direct
-source of the information if known. And finally, the similarity method is to
-find information based on another similar question that already has an answer.
-These 5 strategies vary in their demands for prior knowledge, cognitive
-processing, memory, and time spent. While this theory is aimed at finding
-information in a library setting, scholars have extended the theory to other
-fields and validated the framework [@fidelHumanInformationInteraction2012]; the
-frame is a useful beginning point for my theories of information search through
-network activation or through computer-mediated communication.
-
-Some communication theorists ask why an answer to a question is sought in the
-first place. The Theory of Uncertainty Management
-[@brashersCommunicationUncertaintyManagement2001] professes that people search
-for information when their uncertainty around the subject leads to anxiety or
-other cognitive harms. The Theory of Motivated Information Management
-[@afifiTheoryMotivatedInformation2004; @afifiSeekingInformationSexual2006]
-extends the prior by adding that uncertainty itself is not the catalyst for
-information-search; rather, it is driven by a discrepancy between the current
-level of uncertainty on a subject and desired level of uncertainty. In other
-words, individuals only perform information search when they are distressed by
-their lack of knowledge or understanding on a subject.
-
-One way to find information is to activate network ties to find out information
-through a form of social support. Social support, while previously used
-interchangeably with the term social networks and social integration
-[@houseStructuresProcessesSocial1988], are the emotional, informational, and
-instrumental assistance functions performed between social ties and have strong
-and measurable association with health outcomes
-[@houseMeasuresConceptsSocial1985; @thoitsMechanismsLinkingSocial2011].
-Informational support is the process of seeking “help in defining,
-understanding, and coping with problematic events and include education, advice,
-or referral to another source of support” [@winemiller_etal93, p. 640].
-Brashers, a health communications researcher, defines informational support
-slightly differently, focusing on the exchange of information that “facilitates
-coping with life stresses… that may be exchanged among members of a support
-network” [-@brashersInformationSeekingAvoiding2002, p. 260]. These definitions
-help to differentiate between seeking information through social ties or through
-something anonymous like online search; a need for coping or deeper
-understanding of important matters is thought to sway that decision.
-
-Social support has long been theorized to stem from core discussion networks and
-much of the historical social support surveys only looked at these core
-networks. The underlying assumption is that individuals reach out to a handful
-of strong ties when in need of support, which could be elicited in surveys using
-name generators [@marsdenCoreDiscussionNetworks1987]. This approach has yielded
-important insights, but largely overlooks crucial
-processes of resource activation [@hurlbertCoreNetworksTie2000;
-@perrySocialNetworkActivation2015; @smithDonPutMy2005]. For instance, Small
-[-@smallSomeoneTalk2017] shows that the core discussion network does not capture
-how people activate social support in practice and indicates that people draw on
-much broader social connections for support, reminiscent of the weak ties
-research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
-research investigating how weak-tie support holds for different support types
-based on the architecture put forward by House, Umberson, and Landis
-[-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
-informational support.
-
-However, informational support can also be sought outside of the social network
-context, namely via computer-mediated information search tools such as the
-process of “Googling”. As the online environment began penetrating all facets of
-modern human life, it makes sense that performing online search has become one
-of the most convenient vehicles for information search. While Small
-[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
-simply "happened to be there", online search is theoretically the most
-frictionless and costless mode of support. No social capital or relationship is
-necessary when chosing to utilize a search engine.
-
-There are three computer-mediated vehicles I consider for this analysis: online
-search engines like Google or Bing, posting questions on online forums like
-subreddits or Facebook groups, and posting a status update online via Facebook
-or Twitter. While the first two are largely anonymous and don't require a
-personal network, the third is a unique hybrid between personal network
-connections and online search.
-
-There are important factors that can influence information-seeking strategies
-besides the strength of social capital or ease of search. For instance, we can
-borrow uses and gratifications theory (UGT) from studies of mass communication
-[@blumlerUsesMassCommunications1974; @tanMassCommunicationTheories1985]. UGT
-posits that users are not passive consumers of media and that people have an
-active role in choosing different sources of media based on their satisfaction
-of specific needs on an individual basis. UGT is based on Maslow’s
-[-@maslowTheoryHumanMotivation1943] hierarchy of needs and is compatible with
-Lazarsfeld and Katz’s theory of two-step flow [-@katzPersonalInfluencePart1955]
-because people can choose their media and the opinion leaders they follow.
-Modern-day theorists have extended UGT theory and classified the uses and
-gratifications of the internet and of social media. Stafford, Stafford, and
-Schkade [-@staffordDeterminingUsesGratifications2004] theorize that the internet
-provides gratification through useful content that meets expectations,
-gratification from purposeful navigating or random browsing as a process, and
-social gratification from forming and deepening social ties. Leung
-[-@leungGenerationalDifferencesContent2013] theorizes that social media is
-gratifying for users because it allows for venting of negative feelings,
-provides recognition, provides entertainment, promotes social affection, and
-fulfills cognitive needs.
-
-Adapting these facets of UGT and social support to my own case, I theorize that
-online search allows for increased anonymity, a lowered social cost, and the
-potential avoidance of embarrassment and other negative social interactions,
-especially in the case on search engines. Stephen Rains
-[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
-technical information about an illness online but they then turn to their social
-network for experiential information from others facing similar circumstances in
-the case of cancer. The type of information sought is therefore important.
-If specific expertise on a specific topic is desired by a searcher, they may
-reach out to personal connections that they see as expert such as a doctor, or
-if an individual distrusts the medical establishment, they may be more likely to
-activate informational support among their social network or turn to online
-groups that validate their worldview [@bogersHowSocialAre2014]. Finally, UGT and
-Brasher's definition of social support
-[-@brashersInformationSeekingAvoiding2002] help us to theorize that the
-psychosocial needs like identity management or relational maintenance
-[@brashersInformationSeekingAvoiding2002] of an individual may influence their
-chosen information search vehicle: when the informational need is related to
-forming and deepening social ties search is likely to be done from network ties.
-
-# Research Methodology
+## Research Methodology
 The data used for this research project are based on original survey data
@@
 Science and the Russell Sage Foundation. The main portion of this survey
-replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expanding on
+replicates the book, Someone to Talk To  by expanding on
 Small’s finding that people draw on much broader sources than “important people”
@@
 
-## Measures
-
-###  Sought Information
+### Measures
+
+####  Sought Information
 There are multiple dependent variables of interest for this paper. The first
@@
 Much of the question wording and the specific categories of search were inspired
-by ICPSR project 37220 [@scanlon19].
+by ICPSR project 37220
 
@@
 
-# TODO reorder factors in categorical table
-
-```
-
-### Vaccination Outlook
+## TODO reorder factors in categorical table
+
+```
+
+#### Vaccination Outlook
 
@@
 they had indeed received a vaccination (95% Confidence Interval = \{`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
-closer to 75% [@cdc20], this indicates some bias in our sample that must be
+closer to 75%, this indicates some bias in our sample that must be
 acknowledged: either MTurkers are more likely to be vaccinated that the normal
@@
 who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
-`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
+`r scales::label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
 said they were 'definitely yes' getting the vaccine; 
-`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
+`r scales::label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
 said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
-`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
+`r scales::label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
 said they 'Might or might not', 
-`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
+`r scales::label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
 said 'Probably not', and finally
-`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
+`r scales::label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
 said they would 'definitely not' receive the vaccine. The variable 'Vaccination
@@
 
-### Independent Variables
+#### Independent Variables
 The first independent variables used in this analysis are based on the question, 
@@
 average age of our sample was `r round(mean(rain$age, na.rm = T), 2)`. 
-Our sample was `r label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
-female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
+Our sample was `r scales::label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
+female, and `r scales::label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
 male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
@@
 
-# Analysis
+## Analysis
 
@@
 paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
-fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
+fit a series of Binomial Generalized Linear Models. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r`  ]
 , I fit a logistic regression model predicting
@@
 the relationship between the coefficients and information seeking.^[Figures in 
-this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
+this paper were all created using the `r` packages jtools  and ggplot2
 In Table \@ref(tab:model-2-phi) I disaggregate information seeking behaviors by
@@
 online forum, on a social networking site, or using an online search tool. I
-investigate these differences through a phi coefficient [@warrens08], otherwise
+investigate these differences through a phi coefficient , otherwise
 known as a mean square contingency coefficient which is used to investigate the
 degree of association between two binary variables. ^[To calculate the Phi
-Coefficient, I utilize the Psych `r` package [@psych] ] I then investigate the
+Coefficient, I utilize the Psych `r` package  ] I then investigate the
 associations between my predictors and the 5 information search vehicles by
@@
 
-# Results
+## Results
 ```{r clean_before_reg}
@@
   'age' = 'Age',
-  'gender=Male' = 'Gender, Male',
-  'gender=Other' = 'Gender, Other',
+  'genderMale' = 'Gender, Male',
+  'genderOther' = 'Gender, Other',
+  'female' = 'Gender, Female',
     'college1' = "Associate's Deg or above",
@@
 ```
-## Information Seeking
+### Information Seeking
 ```{r table-model-1}
@@
              'Age' = 'age',
-             'Gender, Male' = 'gender=Male',
-             'Gender, Other' = 'gender=Other',
+             'Gender, Male' = 'genderMale',
+             # 'Gender, Other' = 'genderOther',
              "Associate's Deg or above" = 'college',
@@
              'Hispanic or Latino/x' = 'hispanic'),
-           robust = TRUE) +
-  labs(title = 'What predicts someone intentionally searched for information',
-       caption = 'Exponentiated Coefficients: Scaled and Robust') +
-  ylab("") +
+          robust = TRUE,
+           exp = TRUE) +
+  labs(caption = "Coefficient for 'Gender, Other' not displayed") + 
+  ylab("") + xlab("Exponentiated Coefficients, scaled & robust") + 
   theme_diss() +
-  scale_color_manual(values = my_palette[3])
+  scale_color_manual(values = my_palette[6])
 ```
@@
 additional year of age a person holds they are
-`r label_percent()(exp(mod1$coefficients[['age']])-1)` 
+`r scales::label_percent()(exp(mod1$coefficients[['age']])-1)` 
 more likely to search for information, possibly indicating a generational effect
@@
 
-## Information Search Vehicles
+### Information Search Vehicles
 
@@
       col.names = c("",'Person', 'Dr', 'Online Forum', 'Social Networking Site', 'Online Search')) %>% 
-  kable_styling(latex_options = c("hold_position", "striped"),
-                full_width = F)
+  kable_styling(latex_options = c("hold_position", "striped"))
 
@@
 numbers closer to -1 or positive one indicating a very strong relationship
-[@warrens08]. Table \@ref(tab:model-2-phi) shows the results of these
-coefficients. Out of the five information search vehicles investigated, there is
-evidence that the vehicles are distinctly different concepts because most
-coefficients fall under 0.3, the general rule of thumb for correlation
-coefficients to indicate a relationship. There does seem to be a relationship
-between Online Forums and Social Networking Sites, possibly due to an
-individual's propensity to use online networks over in-person networks. These
-coefficients indicate a weak relationship between any two vehicles of
-information search and that respondents in my sample utilize each of these a
-little bit differently.
+. Table \@ref(tab:model-2-phi) shows...
 
@@
 from an online forum like a subreddit were 
-`r label_percent()(round(exp(part2_models$Doctor$coefficients[['receive_i_fr_onlgroup1']]), 2)-1)`
+`r scales::label_percent()(round(exp(part2_models$Doctor$coefficients[['receive_i_fr_onlgroup1']]), 2)-1)`
 more likely to ask their doctors than those who hadn't ( _p_ < 0.05). Finally, 
 respondents with an associate's degree or higher were 
-`r label_percent()(round(exp(part2_models$Doctor$coefficients[['college1']]), 2)-1)`
+`r scales::label_percent()(round(exp(part2_models$Doctor$coefficients[['college1']]), 2)-1)`
 more likely to ask their doctor for information on the Covid-19 vaccinations
@@
 about the vaccine on a social networking site were 
-`r label_percent()(round(exp(part2_models$Person$coefficients[['receive_i_fr_onlnet1']]), 2)-1)`
+`r scales::label_percent()(round(exp(part2_models$Person$coefficients[['receive_i_fr_onlnet1']]), 2)-1)`
  more likely to seek information from their personal network than those who hadn't 
@@
 I found a racial-ethnic with Hispanic-Latinos; I found that they were about 
-`r label_percent()(exp(part2_models$'Online Forum'$coefficients[['hispanic1']])-1)`
+`r scales::label_percent()(exp(part2_models$'Online Forum'$coefficients[['hispanic1']])-1)`
 more likely to query an online forum than non-Hispanics ( _p_ < 0.05). However, 
@@
 networking site were
-`r label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_onlnet1']]))` 
+`r scales::label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['receive_i_fr_onlnet1']]))` 
 less likely to query a forum than those who hadn't (relative odds ratio =
@@
 Respondents who claimed Asian ancestry were 
-`r label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['race_asian1']]))` 
+`r scales::label_percent()(1-exp(part2_models$'Online Forum'$coefficients[['race_asian1']]))` 
 less likely to query online forum ( _p_ < 0.01).
@@
 Finally, I find that Hispanic-Latinos were 
-`r label_percent()(exp(part2_models$'Social Networking Site'$coefficients[['hispanic1']])-1)`
+`r scales::label_percent()(exp(part2_models$'Social Networking Site'$coefficients[['hispanic1']])-1)`
 more likely to ask their connections on a social networking site about the 
@@
 addition year aged to yield
-`r label_percent()(exp(part2_models$'Online Search'$coefficients[['age']])-1)`
+`r scales::label_percent()(exp(part2_models$'Online Search'$coefficients[['age']])-1)`
 higher odds of searching online ( _p_ < 0.001). The most interesting variations
@@
 Associate's degree or higher were 
-`r label_percent()(1-exp(part2_models$'Online Search'$coefficients[['college1']]))` 
+`r scales::label_percent()(1-exp(part2_models$'Online Search'$coefficients[['college1']]))` 
 less likely to search online for questions about Covid-19 than those with less
 educational attainment ( _p_ < 0.001). In addition, I find that Hispanic-Latinos 
-had `r label_percent()(1-exp(part2_models$'Online Search'$coefficients[['hispanic1']]))` 
+had `r scales::label_percent()(1-exp(part2_models$'Online Search'$coefficients[['hispanic1']]))` 
 lower odds of searching online than non-Hispanics ( _p_ < 0.05).
 
-## Vaccination Views
+### Vaccination Views
 
@@
 like Facebook or Twitter about the vaccines were 
-`r label_percent()(1-round(exp(mod3$coefficients[['receive_i_fr_onlnet1']]), 2))` 
+`r scales::label_percent()(1-round(exp(mod3$coefficients[['receive_i_fr_onlnet1']]), 2))` 
 **less likely** to get vaccinated than those who received no information through
@@
 family or friends with their concerns were 
-`r label_percent()(exp(mod3$coefficients[['int_sought_fr_pers1']])-1)` more likely
+`r scales::label_percent()(exp(mod3$coefficients[['int_sought_fr_pers1']])-1)` more likely
 to become vaccinated ( _p_ < 0.05). Furthermore, my respondents who held an 
@@
              'Hispanic or Latino/x' = 'hispanic'),
-           robust = TRUE) +
-  labs(title = 'Does receiving or searching for information predict vaccination sentiment?', 
-       caption = 'Exponentiated Coefficients: Scaled and Robust') + 
-  ylab("") +
+           robust = TRUE,
+           exp = TRUE) +
+  labs(caption = "Coefficient for 'Gender, Other' not displayed") + 
+  ylab("") + xlab("Exponentiated Coefficients, scaled & robust") + 
   theme_diss()+
-  scale_color_manual(values = my_palette[3])
-```
-
-# Discussion
-Previous research in Sociology and Infodemiology has greatly failed to
-distinguish between the activation of information seeking behaviors online and
-offline. In this paper, I aim to uncover just how different various methods of
-information search are and begin a line of research inquiry that investigates
-the factors associated with each different vehicle. Finally, I also aimed to
-uncover how the different fountains of information and information search
-vehicles hold real world consequences through their associations with Covid-19
-vaccination rates and intentions.
-
-I first find that receiving information about Covid-19 vaccinations from any
-outlined source increases the likelihood of searching out more information. I
-also find important demographic differences in the overall propensity to seek
-out information. First, I find that the older a respondent is, the more likely
-they are to seek out information about Covid-19 vaccinations, possibly
-indicating a larger information need by elderly populations overall, or a more
-pressing need to search for information about the Covid-19 vaccinations because
-of the higher risk of hospitalizations that older populations face
-[@turner_etal18]. Furthermore, I find that those who are college educated were
-more likely to seek out information; for the most part this trend can be
-observed in Table \@ref(tab:table-model-2) as well. Human Capital Theory
-[@mirowsky_ross98] may help to explain this finding; this theory claims that
-higher education can provides the skills to gain health-related knowledge and
-use this knowledge to be proactive in their own lives. Finally, I find that my
-respondents who identified as Black were more likely to seek out further
-information; this may be explained by the maltreatment that African Americans
-have endured in the US healthcare system [@baileyStructuralRacismHealth2017]
-which has led to major distrust of the medical establishment among the
-population [@center2019a; @murray15; @bronson2014don].
-
-Table \@ref(tab:table-model-2) further demonstrated important takeaways about
-how individuals seek information. First, I find that the different information
-seeking vehicles queried in this survey are conceptually different and that the
-utilization of different varies by demographic and supply (information fountain?
-~ source of having receiving information). Overall, receiving information about
-Covid-19 vaccination generally is associated with information seeking behaviors,
-though there are key variations. First, if you received information from a
-doctor, you were likely to search from information from a doctor; this may
-indicate an already existing trusting relationship between patient and
-healthcare provider but it may also indicate the healthcare provider taking
-initiaive and emphasizing the importance of the vaccine or the survey respondent
-seeking out information from an expert. Another important finding is that if you
-received information from a Social Networking Site like Facebook or Twitter, you
-were less likely to query Online Forums like Reddit or Facebook Groups; this may
-be an example of Uses and Gratification Theory
-[@blumlerUsesMassCommunications1974], where the two online platforms may act as
-substitute sources of information and those who were satisfied with the
-information they received on a Social Networking Site didn't have the need to
-seek out more information. Finally, the ethnoracial variations exhibited in
-Table \@ref(tab:table-model-2) likely demonstrate how cultural attitudes around
-the trustworthiness of different sources of information affect the utilization
-of different methods; for example, Asians seem are less likely to use online
-forums than non-Asians while Hispanics are more likely to use them than
-non-Hispanics. The internal variations between the different information search
-vehicles hint at different user profiles and may have major repercussions on the
-quality of information they find and who is exposed to poor quality information.
-
-Given the rampant misinformation around Covid-19, her related vaccinations
-[@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020; 
-@shahsavariConspiracyTimeCorona2020] and the slowed rate of vaccinations in the
-United States, it is important to uncover what relationship the different
-fountains of information and information search vehicles for Covid-19 vaccinations
-are associated with compliance with public health recommendations. Table
-\@ref(tab:table-model-3) demonstrated just how these different fountains of
-information and information search vehicles are associated with real world
-consequences through Covid-19 vaccination rates and intentions. The first
-takeaway is that receiving or seeking information from a doctor or other medical
-profession leads to higher likelihood of completed or planned vaccinations.
-While blanket advice like "Healthcare Providers should recommend the vaccine to
-their patients" would be ineffective because of the declining number of
-Americans with a primary care doctor [@levine_etal20], increasing trust in the
-institution of medicine seems to remain a strong predictor of vaccinations. 
-<!-- add more here, there is a huge logical and sampling fallacy here --> 
-A second major takeaway is that receiving information from a Social Networking
-Site like Facebook timeline or Twitter status update was significantly
-associated with lower vaccination rates. While we don't know what exact
-information was absorbed on these platforms, the lower odds of vaccination
-indicate that it was not positive. Much has been attempted between 2020 and 2022
-to curb vaccine misinformation on these social networking platforms [see
-@bowman20 for an early example]; however, I find evidence that these social
-networking platforms nevertheless have a measurable negative impact. Finally,
-this study also contributes to the conversation on ethnoracial and
-educational differences in vaccine hesitancy. I find in my sample that
-Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
-to receive or plan to receive a vaccination against Covid-19 (Table
-\@ref(tab:table-model-3)). Research in this area has mixed results, with some
-studies showcasing consistent findings to these [@bagasra_etal21; @king_etal21],
-while others show that Whites have the lowest levels of vaccine hesitancy and
-many minorities are much more hesitant [@momplaisir_etal21;
-@foxworth21]. My finding that college-educated respondents were more likely seek
-vaccination is largely consistent with the broader literature
-[@khairat_etal22], though again there are many variations depending on the vaccine
-in question and study context [@siddiqui_etal13].
+  scale_color_manual(values = my_palette[6])
+```
 
@@
   coord_flip()
+
 educ_plot <- rain %>% 
@@
 ```
-
-# Conclusion
-Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline and largely focuses on the
-information that is sent to consumers [push], seeing people as passive receivers
-of information. In this paper, I instead focus on individuals as active agents
-in their search for information to  begin a line of research inquiry that
-investigates the factors associated with the various methods of information
-search.
-
-Given the large swaths of both misinformation and disinformation regarding
-Covid-19 [@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020;
-@shahsavariConspiracyTimeCorona2020] and the measurable impacts this
-misinformation has had on pandemic-related health behaviors
-[@loombaMeasuringImpactCOVID192021], Covid-19 provides an ideal study to
-investigate how we choose to search for information that affects both our own
-lives and the lives of others.
-
-This paper has provided several key findings that can be used to motivate policy
-interventions for the Covid-19 vaccination campaigns and in the future for other
-information campaigns. However, these findings are not to be taken out of the
-context of their limitations. This paper is built off a small survey sample (`r
-nrow(rain)`) that was hosted online and anonymously through MTurk, a service
-that provides people with micro-jobs. Because of how the website is set up,
-respondents are incentivized to fill out surveys as quick as possible and there
-were many responses that were poor quality and removed from the sample before
-analysis. Moreover, there is no incentive for respondents to be honest in these
-surveys. However, each of these limitations are often pointed to as limitations 
-of survey research as a whole.
-
-Overall, this research project is important because the vehicles used in
-information search impacts the information and quality of information found By
-looking at how individuals search, I aim to identify pain points and focus areas
-for future interventions in the misinformation process.
-
-\newpage
-
-# References {-}
-
-<div id="refs"></div>
-
-\newpage
-
-# Appendix 1: Survey Questions
-
--------------------------------------------------
-
-*Q181*: Now, we're going to transition a bit to ask you about the information you received during the Covid-19 pandemic.
-
--------------------------------------------------
-
-*Q170*: In the past 12 months, without searching for it, did you receive information about the Covid-19 vaccine from … (check all sources you received information from)
-
-*	your doctor or other health professional?   (1) 
-*	a person like friend, neighbor, or family member that you know ?  (9) 
-*	From television news channel or the newspaper?  (10) 
-*	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
-*	From a social networking site such as Facebook timeline, Twitter status update, or LinkedIn?  (12) 
-*	Other  (13) _______
-
--------------------------------------------------
-
-*Q171*: And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.
-
-*	Yes  (4) 
-*	No  (5)
-
--------------------------------------------------
-
-*Q172*: How did you look for information about the Covid-19 vaccine?
-
-*	Asking a person like friend, neighbor, or family member that I know  (1) 
-*	Asking my doctor or another health professional  (4) 
-*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
-*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn  (6) 
-*	Searched for my question using an online search engine such as Google or Bing  (7) 
-*	Other  (8) ___________
-
--------------------------------------------------
-
-*Q173*: What sort of information did you search for? 
- Separate different topics with a comma or semi-colon.
-
--------------------------------------------------
-
-*Q174*: How useful was the information you found?
-
-*	Extremely useful  (22) 
-*	Very useful  (23) 
-*	Moderately useful  (24) 
-*	Slightly useful  (25) 
-*	Not at all useful  (26)
-
--------------------------------------------------
-
-*Q175*: Did the information you learned affect your decision to get vaccinated against Covid-19?
-
-*	Yes  (39) 
-*	No  (40)
-
--------------------------------------------------
-
-*Q179*: Did you receive a Covid-19 vaccine?
-
-*	Yes  (9) 
-*	No  (10) 
-*	I'm unsure or would not like to respond  (11)
-
--------------------------------------------------
-
-*Q180*: Do you plan to receive a vaccine for the prevention of the Covid-19 virus?
-
-*	Definitely not  (9) 
-*	Probably not  (10) 
-*	Might or might not  (11) 
-*	Probably yes  (12) 
-*	Definitely yes  (13) 
-*	I would not like to respond  (14)
-
--------------------------------------------------
-
-*gender*: What is your gender?
-
-*	Male  (1) 
-*	Female  (2) 
-*	Other  (3) ________________
-*	Prefer not to say  (4)
-
--------------------------------------------------
-
-*hispanic*: Are you Hispanic, Latino/a/x, or Latin American Origin?
-
-*	Yes  (1) 
-*	No  (2)
-
--------------------------------------------------
-
-*race*: What is your race? If you are "mixed race", select all that apply.
-
-*	White  (1) 
-*	Black or African American  (2) 
-*	American Indian or Alaskan Native  (3) 
-*	Asian (please specify):  (4) _______
-*	Other (please specify):  (5) _______
-*	Prefer not to say  (6)
-
--------------------------------------------------
-
-*educ*: What is the highest level of education that you have completed?
-
-*	Less than high school  (1) 
-*	High school graduate  (2) 
-*	Some college  (3) 
-*	Associate's or Technical degree  (4) 
-*	Bachelor's degree  (5) 
-*	Graduate or professional degree  (6)
-
--------------------------------------------------
-
-*income*: We would be interested to know roughly what your total household income
-before taxes is. We mean income from all sources, including welfare, stock
-dividends, other household members' income, etc. In 2020, in which bracket did your total family income fall?
-
-*	Under $1,000  (1) 
-*	\$1,000 to \$9,999   (2) 
-*	\$10,000 to \$19,999  (3) 
-*	\$20,000 to \$29,999  (4) 
-*	\$30,000 to \$39,999  (5) 
-*	\$40,000 to \$49,999  (6) 
-*	\$50,000 to \$59,999  (7) 
-*	\$60,000 to \$74,999  (8) 
-*	\$75,000 to \$89,999   (9) 
-*	\$90,000 to \$109,999  (10) 
-*	\$110,000 to \$129,999  (11) 
-*	\$130,000 to \$149,999  (12) 
-*	\$150,000 or over  (13) 
-*	Don't know  (14)
-
--------------------------------------------------
-
-*age*: What is your age? (in years)
